---
title: "Summary Tables"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment=NA, prompt=FALSE, cache=FALSE, echo=F, results='asis')

```


```{r loadLibraries, echo = F, message = F}
suppressWarnings({

library(summarytools)
library(knitr)
library(summarytools)
library(dplyr)
})

st_options(bootstrap.css     = FALSE,       # Already part of the theme so no need for it
           plain.ascii       = FALSE,       # One of the essential settings
           style             = "rmarkdown", # Idem.
           dfSummary.silent  = TRUE,        # Suppresses messages about temporary files
           footnote          = NA,          # Keeping the results minimalistic
           subtitle.emphasis = FALSE)       # For the vignette theme, this gives
                                            # much better results. Your mileage may vary

```

```{r load_objects = "asis"}
io <- readRDS("results/multi_city/io.rds")
# Assumes that multi_city_script.R has been run till 
cities <- c('accra','sao_paulo','delhi','bangalore')

# round to
round_to <- 1

# Set plot_mmets to F
plot_mmets <- F

```

## Scenario definition
Table displays highest propensity for each distance category, for a given mode.

Table displays highest propensity (%) for each distance category, for a given mode.

In scenario generation, trips are sampled without replacement to increase the share of the requested mode up to the total shown.

Distance categories are: 

0-1 km = \{trip distance < 2\}

2-5 km = \{2 <= trip distance < 6\}

6+ km = \{6 <= trip distance\}

```{r scen_prop = "asis"}

scen_prop <- round(io$scen_prop, round_to)

rownames(scen_prop) <- paste(rownames(io$scen_prop), "scen", sep = "_")

kable(scen_prop, headings = "Scenario Proportions")

```

## Trip proportion
Case study specific trip proportions by mode, for baseline and five scenarios


```{r load_tidyverse, echo = F, message = F}
suppressWarnings({
  require(tidyverse)  
})
```


```{r trip_mode_dist = "asis", echo = F}

for(city in cities){
  df <- io[[city]]$trip_scen_sets
  df1 <- df %>% dplyr::filter(scenario == "Baseline") %>% group_by(trip_id, trip_mode, scenario)
  u_trips <- df1 %>% distinct(trip_id) %>% nrow()
  td <- df %>% group_by(trip_id, trip_mode, scenario) %>% group_by(trip_mode, scenario) %>% summarise(p = round(dplyr::n() /  u_trips * 100, round_to)) %>% spread(key = trip_mode, value = p) %>% mutate(row_sums = rowSums(.[sapply(., is.numeric)], na.rm = TRUE))
  #td[1:6, 1] <- append('baseline', rownames(scen_prop))
  td <- as.data.frame(t(td))
  names(td) <- lapply(append('baseline', rownames(scen_prop)), as.character)
  td <- td[-1, ]
  print(kable(td, caption = paste("Trip proportion (%) by mode for ", city)))
  cat("\n")
}

```

```{r unload_tidyverse, echo = F, message = F}
suppressWarnings({
  detach("package:tidyverse", character.only = T)
})

```

## Distance tables
Case study specific distance tables for baseline and five scenarios


```{r trip_dist = "asis"}

for(city in cities){
  count_people <- nrow(io[[city]]$synth_pop)
  td <- io[[city]]$dist %>% filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, funs(round((.) / count_people, round_to)))
    colnames(td)[3:7] <- rownames(scen_prop)
    print(kable(td, caption = paste("Distance table (km) for ", city, "( ", count_people, " ) per person")))
    cat("\n")
    
}

```

## Duration tables
Case study specific duration tables for baseline and five scenarios


```{r trip_dur = "asis"}

for(city in cities){
  count_people <- nrow(io[[city]]$synth_pop)
    td <- io[[city]]$dur %>% filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, funs(round((.) / count_people, round_to)))
    colnames(td)[3:7] <- rownames(scen_prop)
    print(kable(td, caption = paste("Duration table (mins) for ", city, "( ", count_people, " ) per person (everyone)")))
    
    
    count_people <- length(unique(io[[city]]$trip_scen_sets$participant_id))
    td <- io[[city]]$dur %>% filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, funs(round((.) / count_people, round_to)))
    colnames(td)[3:7] <- rownames(scen_prop)
    print(kable(td, caption = paste("Duration table (mins) for ", city, "( ", count_people, " ) per person (people with trips)")))
    cat("\n")
}

```

## Physical activity tables
Case study specific physical activity tables for backgound (non-travel) PA, and baseline and five scenarios (non-travel + travel)


```{r mmets = "asis"}

for(city in cities){
  df1 <- as.data.frame(io[[city]]$synth_pop$work_ltpa_marg_met)
  colnames(df1) <- "mmet"
  
  td1 <- df1 %>% filter(mmet == 0) %>% 
    summarise(perct_zeros = round(n() / nrow(df1) * 100, 1))
  
  td2 <- df1 %>%
    summarise(min = min(mmet),
              q_25th = round(quantile(mmet, 0.25), 1),
              median = round(quantile(mmet, 0.50), 1),
              mean = round(mean(mmet), 1),
              q_75th = round(quantile(mmet, 0.75), 1),
              q_90th = round(quantile(mmet, 0.95), 1),
              max = round(max(mmet), 1))
  
  td3 <- cbind(td1, td2)
  td3 <- as.data.frame(t(td3))
  
  df2 <- select(io[[city]]$outcomes$mmets, base_mmet : scen5_mmet)
  
  td4 <- df2 %>% gather(key = "scenario", value = "mmet") %>% 
    filter(mmet == 0) %>% 
    group_by(scenario) %>% 
    summarise(perct_zeros = round(n() / nrow(df2) * 100, 1))
  
  td5 <- df2 %>% gather(key = "scenario", value = "mmet") %>% 
    group_by(scenario) %>% 
    summarise(min = min(mmet),
              q_25th = round(quantile(mmet, 0.25), 1),
              median = round(quantile(mmet, 0.50), 1),
              mean = round(mean(mmet), 1),
              q_75th = round(quantile(mmet, 0.75), 1),
              q_90th = round(quantile(mmet, 0.95), 1),
              max = round(max(mmet), 1))
  
  td6 <- left_join(td4, td5, "scenario")
  td6 <- as.data.frame(t(td6))
  td6 <- td6[-1,]
  td6 <- mutate_all(td6, function(x) as.numeric(as.character(x)))

  td <- cbind(td3, td6)
  
  colnames(td)[1] <- "Background (non-travel)"
  colnames(td)[2] <- "Baseline"
  colnames(td)[3:7] <- rownames(scen_prop)
  
  print(kable(td, caption = paste("Marginal MET-h/wk for ", city)))
  cat("\n")
}

```

```{r pa, echo = F, message = F}

if (plot_mmets){

  dfSummary(accra_mmets <- io[["accra"]]$outcomes$mmets, style = 'grid', graph.magnif = 0.75, tmp.img.dir = "/tmp")
  
  dfSummary(sao_paulo_mmets <- io[["sao_paulo"]]$outcomes$mmets, style = 'grid', graph.magnif = 0.75, tmp.img.dir = "/tmp")
  
  dfSummary(delhi_mmets <- io[["delhi"]]$outcomes$mmets, style = 'grid', graph.magnif = 0.75, tmp.img.dir = "/tmp")
  
  dfSummary(bangalore_mmets <- io[["bangalore"]]$outcomes$mmets, style = 'grid', graph.magnif = 0.75, tmp.img.dir = "/tmp")
}

```
