---
title: "Summary Tables"
output: html_document
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment=NA, prompt=FALSE, cache=FALSE, echo=F, results='asis')

```


```{r loadLibraries, echo = F, message = F}
suppressWarnings({

library(summarytools)
library(knitr)
library(summarytools)
library(tidyverse)
})

st_options(bootstrap.css     = FALSE,       # Already part of the theme so no need for it
           plain.ascii       = FALSE,       # One of the essential settings
           style             = "rmarkdown", # Idem.
           dfSummary.silent  = TRUE,        # Suppresses messages about temporary files
           footnote          = NA,          # Keeping the results minimalistic
           subtitle.emphasis = FALSE)       # For the vignette theme, this gives
                                            # much better results. Your mileage may vary

```

```{r load_objects = "asis", echo = F, message = F}
io <- readRDS("results/multi_city/io.rds")
# Assumes that multi_city_script.R has been run till 
cities <- c('accra','sao_paulo','delhi','bangalore', 'santiago', 'belo_horizonte', 'buenos_aires', 'mexico_city','bogota', 'cape_town', 'vizag')

# cities <- c('sao_paulo')

# Read trip_order
trip_order <- read_csv("data/global/trips/mode_order.csv")

# round to
round_to <- 1

# Set plot_mmets to F
plot_mmets <- F

```

## Scenario definition
Table displays highest propensity for each distance category, for a given mode.

Table displays highest propensity (%) for each distance category, for a given mode.

In scenario generation, trips are sampled without replacement to increase the share of the requested mode up to the total shown.

Distance categories are: 

0-1 km = \{trip distance < 2\}

2-5 km = \{2 <= trip distance < 6\}

6+ km = \{6 <= trip distance\}

```{r scen_prop = "asis"}

scen_prop <- round(io$scen_prop, round_to)

rownames(scen_prop) <- paste(rownames(io$scen_prop), "scen", sep = "_")

kable(scen_prop, headings = "Scenario Proportions")

```

## Case study specific propensities


|accra|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 96.7|66.2|2.0 |
| bicycle | 0.6|0.3|0.4 |
| car | 1.0|10.4|16.9 |
| motorcycle | 0.2|0.9|2.7 |
| bus | 0.0|18.6|69.4 |

|sao_paulo|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 65.4|6.9|2.9 |
| bicycle | 0.7|0.9|0.3 |
| car | 22.2|41.9|27.2 |
| motorcycle | 1.3|2.7|3.5 |
| bus | 9.7|43.0|35.8 |

|delhi|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 84.3|11.1|0.8 |
| bicycle | 1.9|7.9|3.6 |
| car | 1.9|14.7|19.6 |
| motorcycle | 5.6|31.9|25.3 |
| bus | 0.7|19.7|35.5 |

|bangalore|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 89.7|28.6|1.2 |
| bicycle | 2.6|10.9|0.9 |
| car | 0.8|5.0|4.9 |
| motorcycle | 4.8|37.3|48.2 |
| bus | 0.6|8.3|29.3 |

|santiago|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 92.5|29.7|0.3 |
| bicycle | 1.5|10.5|2.5 |
| car | 5.4|42.3|27.4 |
| motorcycle | 0.0|0.6|0.7 |
| bus | 0.0|3.1|36.0 |

|belo_horizonte|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 91.7|36.0|0.6 |
| bicycle | 0.4|3.6|1.0 |
| car | 7.2|39.9|38.9 |
| motorcycle | 0.2|6.6|7.3 |
| bus | 0.0|0.9|39.4 |

|buenos_aires|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 95.9|32.9|0.2 |
| bicycle | 3.0|10.1|1.5 |
| car | 0.5|24.1|25.4 |
| motorcycle | 0.0|2.2|1.7 |
| bus | 0.6|27.4|49.9 |

|mexico_city|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 95.4|38.1|0.3 |
| bicycle | 0.8|7.7|1.3 |
| car | 2.3|23.9|28.6 |
| motorcycle | 0.0|3.3|1.9 |
| bus | 0.3|19.0|48.2 |

|bogota|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 90.0|27.3|2.4 |
| bicycle | 4.5|15.1|4.2 |
| car | 1.4|13.3|18.7 |
| motorcycle | 0.4|5.6|7.2 |
| bus | 3.2|34.1|62.9 |

|cape_town|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 88.5|23.3|2.0 |
| bicycle | 0.0|0.4|0.3 |
| car | 9.4|46.1|47.3 |
| motorcycle | 0.0|0.3|0.6 |
| bus | 2.0|27.5|36.5 |

|vizag|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| walking | 81.4|19.6|0.1 |
| bicycle | 3.9|7.6|1.9 |
| car | 0.6|2.5|2.2 |
| motorcycle | 9.6|25.4|22.9 |
| bus | 0.1|21.7|56.1 |


## Trip proportion
Case study specific trip proportions by mode, for baseline and five scenarios


```{r load_tidyverse, echo = F, message = F}
suppressWarnings({
  require(tidyverse)  
})
```


```{r trip_mode_dist = "asis", echo = F}

for(city in cities){
  print(city)
  df <- io[[city]]$trip_scen_sets
  u_trips <- df %>% dplyr::filter(scenario == "Baseline") %>% summarise(uid <- n_distinct(trip_id)) %>% as.numeric()
  td <- df %>% distinct(trip_id, scenario, .keep_all = T) %>% group_by(trip_mode, scenario) %>% summarise(p = round(dplyr::n() / u_trips * 100, 1)) %>% spread(key = trip_mode, value = p) %>% mutate(row_sums = rowSums(.[sapply(., is.numeric)], na.rm = TRUE))
  td <- as.data.frame(t(td))
  names(td) <- lapply(append('baseline', rownames(scen_prop)), as.character)
  td <- td[-1, ]
  x <- match(row.names(td), trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]
  
  print(kable(td, caption = paste("Trip proportion (%) by mode for ", city)))
  cat("\n")
}

```

```{r unload_tidyverse, echo = F, message = F}
suppressWarnings({
  detach("package:tidyverse", character.only = T)
})

```

## Distance tables
Case study specific distance tables for baseline and five scenarios


```{r trip_dist = "asis"}

for(city in cities){
  count_people <- nrow(io[[city]]$synth_pop)
  td <- io[[city]]$dist %>% filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, list(~round((.) / count_people, round_to)))
  colnames(td)[3:7] <- rownames(scen_prop)
  
  x <- match(td$stage_mode, trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]
  row.names(td) <- NULL
  
  print(kable(td, caption = paste("Distance table (km) for ", city, "( ", count_people, " ) per person")))
  cat("\n")
  
  
  count_people <- length(unique(io[[city]]$trip_scen_sets$participant_id))
  td <- io[[city]]$dist %>% filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, list(~round((.) / count_people, round_to)))
  colnames(td)[3:7] <- rownames(scen_prop)
  x <- match(td$stage_mode, trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]
  row.names(td) <- NULL
  
  print(kable(td, caption = paste("Distance table (mins) for ", city, "( ", count_people, " ) per person (people with trips)")))
  
}

```

## Distance by distance category
### Tables

```{r trip_dist_mode_figs = "asis"}

for (city in cities){
  
  df <- io[[city]]$trip_scen_sets %>% filter(scenario == 'Baseline') %>% distinct(trip_id, .keep_all = T) %>% group_by(trip_distance_cat) %>% summarise(sum_dist = sum(trip_distance), n_vals = n(), prop = round(n_vals / nrow(.) * 100, 1))
  print(kable(df, caption = paste("Distance by mode by for  ", city)))
}

```

<!-- ### Figures -->

<!-- ```{r trip_dist_mode_figs = "asis"} -->

<!-- for (city in cities){ -->

<!--   df <- io[[city]]$trip_scen_sets %>% filter(scenario == 'Baseline' & trip_mode %in% c('walking', 'bicycle', 'car', 'motorcycle', 'bus')) %>% distinct(trip_id, .keep_all = T) %>% group_by(trip_mode, trip_distance_cat) %>% summarise(sum_dist = sum(trip_distance), n_vals = n()) %>%  -->
<!--     group_by(trip_mode) %>% mutate(n_vals_1 = sum(n_vals)) %>%  -->
<!--     mutate(prop = round(n_vals/n_vals_1 * 100, 1)) -->

<!--   print(ggplot(data=df, aes(x=trip_distance_cat, y=prop)) + -->
<!--           geom_bar(stat="identity", fill="steelblue")+ -->
<!--           facet_wrap(vars(trip_mode)) + -->
<!--           geom_text(aes(label=prop), vjust = -0.3, size = 3.5)+ -->
<!--           theme_minimal() + -->
<!--           theme(panel.spacing = unit(2, "lines")) + -->
<!--           labs(title = paste(city, ' by dist by mode'))) -->
<!-- } -->




<!-- ``` -->


## Duration tables
Case study specific duration tables for baseline and five scenarios


```{r trip_dur = "asis"}

for(city in cities){
  count_people <- nrow(io[[city]]$synth_pop)
  td <- io[[city]]$dur %>% filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, list(~round((.) / count_people, round_to)))
  colnames(td)[3:7] <- rownames(scen_prop)
  
  x <- match(td$stage_mode, trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]
  row.names(td) <- NULL
  
  print(kable(td, caption = paste("Duration table (mins) for ", city, "( ", count_people, " ) per person (everyone)")))
  
  
  count_people <- length(unique(io[[city]]$trip_scen_sets$participant_id))
  td <- io[[city]]$dur %>% filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, list(~round((.) / count_people, round_to)))
  colnames(td)[3:7] <- rownames(scen_prop)
  
  x <- match(td$stage_mode, trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]
  row.names(td) <- NULL
  
  print(kable(td, caption = paste("Duration table (mins) for ", city, "( ", count_people, " ) per person (people with trips)")))
  cat("\n")
}

```

## Physical activity tables
Case study specific physical activity tables for backgound (non-travel) PA, and baseline and five scenarios (non-travel + travel)


```{r mmets = "asis"}

for(city in cities){
  df1 <- as.data.frame(io[[city]]$synth_pop$work_ltpa_marg_met)
  colnames(df1) <- "mmet"
  
  td1 <- df1 %>% filter(mmet == 0) %>% 
    summarise(perct_zeros = round(dplyr::n() / nrow(df1) * 100, 1))
  
  td2 <- df1 %>%
    summarise(min = min(mmet),
              q_25th = round(quantile(mmet, 0.25), 1),
              median = round(quantile(mmet, 0.50), 1),
              mean = round(mean(mmet), 1),
              q_75th = round(quantile(mmet, 0.75), 1),
              q_90th = round(quantile(mmet, 0.95), 1),
              max = round(max(mmet), 1))
  
  td3 <- cbind(td1, td2)
  td3 <- as.data.frame(t(td3))
  
  df2 <- select(io[[city]]$outcomes$mmets, base_mmet : scen5_mmet)
  
  td4 <- df2 %>% gather(key = "scenario", value = "mmet") %>% 
    filter(mmet == 0) %>% 
    group_by(scenario) %>% 
    summarise(perct_zeros = round(dplyr::n() / nrow(df2) * 100, 1))
  
  td5 <- df2 %>% gather(key = "scenario", value = "mmet") %>% 
    group_by(scenario) %>% 
    summarise(min = min(mmet),
              q_25th = round(quantile(mmet, 0.25), 1),
              median = round(quantile(mmet, 0.50), 1),
              mean = round(mean(mmet), 1),
              q_75th = round(quantile(mmet, 0.75), 1),
              q_90th = round(quantile(mmet, 0.95), 1),
              max = round(max(mmet), 1))
  
  td6 <- left_join(td4, td5, "scenario")
  td6 <- as.data.frame(t(td6))
  td6 <- td6[-1,]
  td6 <- mutate_all(td6, function(x) as.numeric(as.character(x)))

  td <- cbind(td3, td6)
  
  colnames(td)[1] <- "Background (non-travel)"
  colnames(td)[2] <- "Baseline"
  colnames(td)[3:7] <- rownames(scen_prop)
  
  print(kable(td, caption = paste("Marginal MET-h/wk for ", city)))
  cat("\n")
}

```

```{r pa, echo = F, message = F}

if (plot_mmets){

  dfSummary(accra_mmets <- io[["accra"]]$outcomes$mmets, style = 'grid', graph.magnif = 0.75, tmp.img.dir = "/tmp")
  
  dfSummary(sao_paulo_mmets <- io[["sao_paulo"]]$outcomes$mmets, style = 'grid', graph.magnif = 0.75, tmp.img.dir = "/tmp")
  
  dfSummary(delhi_mmets <- io[["delhi"]]$outcomes$mmets, style = 'grid', graph.magnif = 0.75, tmp.img.dir = "/tmp")
  
  dfSummary(bangalore_mmets <- io[["bangalore"]]$outcomes$mmets, style = 'grid', graph.magnif = 0.75, tmp.img.dir = "/tmp")
}

```
