---
title: "Summary Tables ITHIMR"
author: "Rahul Goel, MRC Epidemiology Unit, University of Cambridge, UK"
date: "25 April 2019"
output:
  pdf_document: default
  html_document: default
  word_document: default
---


# Introduction
These are the summary tables of the following items
1) Individual-level PM2.5 concentrations for baseline and scenarios
2) Individual-level physical activity for baseline and scenarios
3) Distance mode shares for baseline and scenarios


```{r, echo=FALSE}
#setwd('C:/Users/rg574/Dropbox/spatiotemporal analysis fatalities inida/Rajasthan tourism road deaths') #to create pretty tables
```

```{r, message=FALSE, warning=FALSE}
#library(INLA)     #loading the INLA package
library(ggplot2)  #loading ggplot package for plotting graphs
library(knitr)     
library(tidyr)
library(dplyr)

```


# Boxplots of Individual-level PM2.5 Concentrations

```{r, message=FALSE, warning=FALSE, echo=FALSE}
io <- readRDS("V:/Group/RG_PHM/ITHIM-R/results/multi_city/io.rds")

cities<- names(io)
cities<- cities[-2]

for (x in 1: length(cities))
{
  names(io[[cities[x]]]$outcomes$pm_conc_pp)[6:11]<-c("baseline","walk_scen", "bike_scen", "car_scen", "MC_scen", "bus_scen")
  data_long <- gather(io[[cities[x]]]$outcomes$pm_conc_pp, scenario, pm_conc, baseline:bus_scen, factor_key=TRUE)
  x<-ggplot(data_long, aes(x=scenario, y=pm_conc, fill=scenario)) + geom_boxplot()+ ggtitle(cities[x])+ labs(y="Daily PM2.5 Concentration", x = "Scenarios")
  print(x)
  
}
```




# Descriptive tables of Individual-level PM2.5 Concentrations

```{r, message=FALSE, warning=FALSE, echo=FALSE}

for (x in 1: length(cities))
{
  names(io[[cities[x]]]$outcomes$pm_conc_pp)[6:11]<-c("baseline","walk_scen", "bike_scen", "car_scen", "MC_scen", "bus_scen")
  data_long <- gather(io[[cities[x]]]$outcomes$pm_conc_pp, scenario, pm_conc, baseline:bus_scen, factor_key=TRUE)
  summary<- as.data.frame(data_long %>% group_by(scenario) %>% summarise('mean'=mean(pm_conc),'5th'=quantile(pm_conc, 0.05),'50th'=quantile(pm_conc, 0.5),'95th'=quantile(pm_conc, 0.9)))
  summary<- cbind(summary$scenario ,round(summary[,2:5], digits=1))
  names(summary)[1]<-"Scenario"
  print (as.character(cities[[x]]))
  print(summary)
  

  
}
```


# Boxplots of Individual-level Physical activity (MMETs)

```{r, message=FALSE, warning=FALSE, echo=FALSE}


for (x in 1: length(cities))
{
  names(io[[cities[x]]]$outcomes$mmets)[5:10]<-c("baseline","walk_scen", "bike_scen", "car_scen", "MC_scen", "bus_scen")
  data_long <- gather(io[[cities[x]]]$outcomes$mmets, scenario, mmet, baseline:bus_scen, factor_key=TRUE)
  x<-ggplot(data_long, aes(x=scenario, y=mmet, fill=scenario)) + geom_boxplot()+ ggtitle(cities[x])+ labs(y="Weekly MMET", x = "Scenarios")
  print(x)
  
}
```

# Descriptive tables of Individual-level Physical activity (MMETs)

```{r, message=FALSE, warning=FALSE, echo=FALSE}

for (x in 1: length(cities))
{
  names(io[[cities[x]]]$outcomes$mmets)[5:10]<-c("baseline","walk_scen", "bike_scen", "car_scen", "MC_scen", "bus_scen")
  data_long <- gather(io[[cities[x]]]$outcomes$mmets, scenario, mmet, baseline:bus_scen, factor_key=TRUE)
  summary<- as.data.frame(data_long %>% group_by(scenario) %>% summarise('mean'=mean(mmet),'5th'=quantile(mmet, 0.05),'50th'=quantile(mmet, 0.5),'95th'=quantile(mmet, 0.9)))
  summary<- cbind(summary$scenario ,round(summary[,2:5], digits=1))
  names(summary)[1]<-"Scenario"
  print (as.character(cities[[x]]))
  print(summary)
  

  
}
```


# Distance share by scenarios in percentages (excludes city-specific minority modes-- auto rickshaws, subway, etc.)

```{r, message=FALSE, warning=FALSE, echo=FALSE}
for (x in 1: length(cities))
{
  
select<- c("car", "motorcycle", "walking", "bicycle", "bus")
io[[cities[x]]]$trip_scen_sets <-io[[cities[x]]]$trip_scen_sets[io[[cities[x]]]$trip_scen_sets$trip_mode %in% select,]

dist_scen<- io[[cities[x]]]$trip_scen_sets %>% group_by(trip_mode, scenario) %>% summarise(sum(trip_distance))
dist_scen<- as.data.frame (dist_scen)
names(dist_scen)[3]<-"distance"
dist_scen<-spread(dist_scen, trip_mode, distance)
dist_scen$sum<-rowSums (dist_scen[2:(ncol(dist_scen)-1)], na.rm = FALSE, dims = 1)
dist_scen_prop<- round(dist_scen[,2:(ncol(dist_scen)-1)]*100/dist_scen$sum, digits=1)
dist_scen_prop<- cbind(dist_scen[,1], dist_scen_prop)

names(dist_scen_prop)[1]<-"Scenario"
dist_scen_prop$Scenario<- c("baseline","walk_scen", "bike_scen", "car_scen", "MC_scen", "bus_scen")
print (as.character(cities[[x]]))
print(dist_scen_prop)
#library(knitr)
#library(kableExtra)
#kable(dist_scen_prop)
}
```
