---
#title: "AP/PA Tables ITHIM Global"
title: "AP/PA Tables ITHIM Global"
date: "`r format(Sys.time(), '%d %B, %Y')`"
params:
  output_version: ''
execute: 
  cache: true
output:
  html_document: 
    toc: true
    toc_depth: 5
    toc_float: true
  word_document: default
  pdf_document: default
  
format:
  html: 
    fig-format: svg
    
code-link: true
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment=NA, prompt=FALSE, cache=FALSE, echo=F, results='asis', dev = 'svg')

# Script to summarise the PM2.5 personal exposure levels, PM2.5 and CO2 emissions and physical activity levels

# This script looks at individual level PM2.5 exposure for all scenarios, it summarise the PM2.5 and CO2 concentration levels for all scenarios and summarises the individual physical activity levels for all scenarios. 



#### It produces the following output documents:


### - html file containing the following information:

# - boxplots for each city of daily individual PM2.5 exposure levels for each scenario 

# - one table for each city detailing the individual PM2.5 exposure levels including the mean, 5th, 50th and 95th percentiles, the mean PM2.5 concentration levels for each scenario and the change in PM2.5 compared to the reference scenario

# - one table detailing the percentage Baseline PM2.5 emissions attributed to each transport mode, the city wide PM2.5 concentration levels and the percentage of these emissions attributed to transport for all cities

# - one table detailing the Baseline CO2 concentration levels for each scenario for all cities

# - boxplots for each city of individual mMET physical activity levels for each scenario  

# - one table for each city giving the mean, 5th, 50th and 95th percentile levels of individual physical activity levels (mMETs) for each scenario

# - one table detailing the average mMETs levels for each scenario for all cities 

# 2nd Option:

# - boxplots for each city of daily individual PM2.5 exposure levels for each scenario 

# - one table detailing the Baseline PM2.5 emissions for each mode, the city wide PM2.5 concentration levels and the percentage of these emissions attributed to transport for all cities

# - one table for each city detailing the individual PM2.5 exposure levels including the mean, 5th, 50th and 95th percentiles, the mean PM2.5 concentration levels for each scenario and the change in PM2.5 compared to the reference scenario. Table also contains CO2 emissions for each scenario

# - boxplots for each city of individual mMET physical activity levels for each scenario 



### - output .csv/.xlsx files containing the following information:

# - desc_stats.csv file (results/multi_city/AP/desc_stats.csv, also saved with output_version number in file name) containing the summary statistics of individual PM2.5 exposure levels, the total PM2.5 emissions levels, the change in PM2.5 concentration levels compared to the reference scenario and the total transport related CO2 emission emissions for each scenario and city


# - desc_stats_*output_version*.xlsx file (results/multi_city/AP/desc_stats_*output_version*.xlsx) containing the following tabs:

#   - PM_2.5_emission_inventory: table detailing the percentage Baseline PM2.5 emissions attributed to each transport mode, the city wide PM2.5 concentration levels and the percentage of these emissions attributed to transport for all cities

#   - C02_emission_inventory: table detailing the CO2 emission levels for each scenario for all cities

#   - summary_stats_PM2.5_CO2: summary statistics of individual PM2.5 exposure levels, the total PM2.5 emissions levels, the change in PM2.5 concentration levels compared to the reference scenario and the total transport related CO2 emission emissions for each scenario and city






#### The script performs the following steps, assuming that the ITHIM-Global model has been run in CONSTANT mode and the ithim_objects object has been saved in "results/multi_city/io.rds":

# - read in input parameter values and define function that renames the existing scenarios

# - create boxplots of individual PM2.5 levels for each scenario, one for each city, and write to the .html file

# - create one table for each city detailing the individual PM2.5 exposure levels incl. the mean, 5th, 50th and 95th percentiles, the mean PM2.5 concentration levels for each scenario and the change in PM2.5 compared to the reference scenario

# - create a single table detailing the percentage Baseline PM2.5 emissions attributed to each mode, the city wide PM2.5 concentration levels and the percentage of these emissions attributed to transport for all cities

# - create a single summary table showing the CO2 emissions in each scenario for all cities

# - create boxplots for each city showing the individual mMET levels for each scenario

# - create one table for each city giving the mean, 5th, 50th and 95th percentile levels of individual physical activity levels (mMETs) for each scenario

# - create a single table detailing the average mMETs levels for each scenario for all cities 



# - 2nd option:

# - create boxplots for each city of daily individual PM2.5 exposure levels for each scenario 

# - create one table detailing the Baseline PM2.5 emissions for each mode, the city wide PM2.5 concentration levels and the percentage of these emissions attributed to transport for all cities

# - create one table for each city detailing the individual PM2.5 exposure levels including the mean, 5th, 50th and 95th percentiles, the mean PM2.5 concentration levels for each scenario and the change in PM2.5 compared to the reference scenario. Table also contains CO2 emissions for each scenario

# - create boxplots for each city of individual mMET physical activity levels for each scenario 



```



```{r, message=FALSE, warning=FALSE}
#library(INLA)     #loading the INLA package
library(ggplot2)  #loading ggplot package for plotting graphs
library(knitr)     
library(tidyverse)
library(readxl)
library(cli)

theme_set(theme_minimal())

```


```{r, message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE}

###### Read in input parameters
#output_version <- 
#

if (!exists("output_version")){
  ## Get the current repo sha
  gitArgs <- c("rev-parse", "--short", "HEAD", ">", file.path("repo_sha"))
  # Use shell command for Windows as it's failing with system2 for Windows (giving status 128)
  if (.Platform$OS.type == "windows"){
    shell(paste(append("git", gitArgs), collapse = " "), wait = T)
  } else {
    system2("git", gitArgs, wait = T)
  }
  
  repo_sha <-  as.character(readLines(file.path("repo_sha")))
  output_version <- paste0(repo_sha, "_test_run")
} 

# Assumes that multi_city_script.R has been run  
# read in input file
io <- readRDS(paste0("results/multi_city/io_", output_version, ".rds"))

# define which decimal place to round to
round_to <- 2

# Get names of cities from the io object
cities <- names(io)[!names(io) %in% c('scen_prop','ithim_run' )]

# Plot colours for each scenario
scen_colours <- c("Baseline" = '#b15928',
                  "Cycling" = '#abdda4',
                  "Car" = '#d7191c',
                  "Bus" = '#2b83ba',
                  "Motorcycle" = '#fdae61')


# function to convert scenario names
get_qualified_scen_name <- function(cs){
  qualified_scen_name <- ""
  if (cs == 'base' | cs == 'Baseline' | cs == 'baseline')
    qualified_scen_name <- 'Baseline'
  else if(cs == "sc_walk")
    qualified_scen_name <- 'Walk'
  else if(cs == "sc_cycle" | cs == "Bicycling")
    qualified_scen_name <- 'Cycling'
  else if(cs == "sc_car" | cs == "Car")
    qualified_scen_name <- 'Car'
  else if(cs == "sc_motorcycle")
    qualified_scen_name <- 'Motorcycling'
  else if(cs == "sc_bus" | cs == "Public Transport")
    qualified_scen_name <- 'Bus'
  
  return(qualified_scen_name)
}


# initialise parameters using first city in list
city <- cities[1]
scen_length <- length(io$ithim_run$scenario_names) - 1

# input parameter file name
input_parameter_file <<- io$ithim_run$input_parameter_file
  
# scenario and reference scenario definitions
scenario_name <- io$ithim_run$scenarios_used
ref_scen <- io$ithim_run$reference_scenario
reference_scenario <- get_qualified_scen_name(ref_scen)

# further model run information
compute_mode <- io$ithim_run$compute_mode 
timestamp_model <- io$ithim_run$timestamp
comments_model <- io$ithim_run$comment

# read in local input parameter inputs
all_inputs <- read_excel(input_parameter_file, sheet = "all_city_parameter_inputs")
all_inputs[is.na(all_inputs)] <- ""
all_inputs <- as.data.frame(all_inputs)

# get input parameters into correct format
parameter_names <- all_inputs$parameter
parameter_starts <- which(parameter_names!='')
parameter_stops <- c(parameter_starts[-1] - 1, nrow(all_inputs)) 
parameter_names <- parameter_names[parameter_names!='']
parameter_list <- list()

# extract local parameter information
for(i in 1:length(parameter_names)){
  parameter_list[[parameter_names[i]]] <- list()
  parameter_index <- which(all_inputs$parameter==parameter_names[i]) 
  if(all_inputs[parameter_index,2]=='')  { 
    parameter_list[[parameter_names[i]]] <- lapply(cities,function(x) {
      city_index <- which(colnames(all_inputs)==x)
      val <- all_inputs[parameter_index,city_index]
      ifelse(val%in%c('T','F'),val,ifelse(is.numeric(val), as.numeric(val), as.character(val)))
    })
    names(parameter_list[[parameter_names[i]]]) <- cities
  }else if(all_inputs[parameter_index,2]=='constant'){
    if (compute_mode != 'sample'){
      indices <- 0
      parameter_list[[parameter_names[i]]] <- lapply(cities,function(x) {
        city_index <- which(colnames(all_inputs)==x)
        val <- all_inputs[parameter_index+indices,city_index]
        ifelse(val=='',0,as.numeric(val))
      })
    }
    if(compute_mode=='sample'){ # if sampling from distribution, check that distribution parameters exist
      parameter_list[[parameter_names[i]]] <- lapply(cities,function(x) {
        indices <- 1:2
        city_index <- which(colnames(all_inputs)==x)  
        val <- all_inputs[parameter_index+indices,city_index] 
        if (val[1] == '' & val[2]==''){  # if no distribution parameters given in input file, read in constant value instead
          indices <-0
          city_index <- which(colnames(all_inputs)==x) 
          val <- all_inputs[parameter_index+indices,city_index]} 
        val <- as.numeric(val)
      })
    }
    names(parameter_list[[parameter_names[i]]]) <- cities
  }else{
    parameter_list[[parameter_names[i]]] <- lapply(cities,function(x) {
      city_index <- which(colnames(all_inputs)==x)
      if(any(all_inputs[parameter_starts[i]:parameter_stops[i],city_index]!='')){
        sublist_indices <- which(all_inputs[parameter_starts[i]:parameter_stops[i],city_index]!='')
        thing <- as.list(as.numeric(c(all_inputs[parameter_starts[i]:parameter_stops[i],city_index])[sublist_indices]))
        names(thing) <- c(all_inputs[parameter_starts[i]:parameter_stops[i],2])[sublist_indices]
        thing
      }
    }
    )
    names(parameter_list[[parameter_names[i]]]) <- cities
  }
}

list2env(parameter_list, environment()) 


# read in global parameters
all_global_inputs <- read_excel(input_parameter_file, sheet = "all_global_parameter_inputs")
all_global_inputs[is.na(all_global_inputs)] <- ""
all_global_inputs <- as.data.frame(all_global_inputs)

# get input parameters into correct format
global_parameter_names <- all_global_inputs$parameter
global_parameter_starts <- which(global_parameter_names!='')
global_parameter_stops <- c(global_parameter_starts[-1] - 1, nrow(all_global_inputs)) 
global_parameter_names <- global_parameter_names[global_parameter_names!='']
global_parameter_list <- list()

# extract global parameter information
for(i in 1:length(global_parameter_names)){
  global_parameter_list[[global_parameter_names[i]]] <- list()
  global_parameter_index <- which(all_global_inputs$parameter==global_parameter_names[i]) 
  if(all_global_inputs[global_parameter_index,2]=='')  { 
    
    global_parameter_list[[global_parameter_names[i]]] <- all_global_inputs[global_parameter_index,'global']
    
  }else if(all_global_inputs[global_parameter_index,2]=='constant'){
    if (compute_mode != 'sample'){
      global_parameter_list[[global_parameter_names[i]]] <- ifelse(all_global_inputs[global_parameter_index,'global']=='',
                                                                   0,as.numeric(all_global_inputs[global_parameter_index,'global']))
    }
    else if(compute_mode=='sample'){ # if sampling from distribution, check that distribution parameters exist
      indices <- 1:2
      val <- all_global_inputs[global_parameter_index+indices,'global'] 
      if (val[1] == '' & val[2]==''){  # if no distribution parameters given in input file, read in constant value instead
        val <- all_global_inputs[global_parameter_index,'global']} 
      val <- as.numeric(val)
      global_parameter_list[[global_parameter_names[i]]] <- val
    }
  }
}

list2env(global_parameter_list, environment()) 

# get parameters into correct format
dist_cat <- unlist(strsplit(gsub(" ", "", dist_cat, fixed = TRUE), "\\,"))


min_age <- as.numeric(min_age)
max_age <- as.numeric(max_age)

day_to_week_scalar <- as.numeric(day_to_week_scalar)



# print model run information to screen:
cat(
   cli::style_hyperlink(
      text = paste0("https://github.com/ITHIM/ITHIM-R/tree/", stringr::str_remove(output_version, "_test_run")),
      url = paste0("https://github.com/ITHIM/ITHIM-R/tree/", stringr::str_remove(output_version, "_test_run"))
   )
)
cat("  \n")
cat(paste0('Scenario: ', SCENARIO_INCREASE * 100, "%")) 
cat("  \n")
cat(paste0('Input Parameter version: ', io$ithim_run$input_parameter_file)) 
cat("  \n")
cat(paste0('Output version: ', output_version)) 
cat("  \n")
cat(paste0('Timestamp of model run: ', timestamp_model))
cat("  \n")
cat(paste0('Comments from model run: ', comments_model))
cat("  \n")

```


# Introduction
These are the summary tables of the following items

1) Individual PM2.5 exposure levels and total PM2.5 emissions for baseline and scenarios
2) Overall CO2 emissions for baseline and scenarios
3) Individual physical activity levels (mMETs) for baseline and scenarios



# Boxplots of individual daily PM2.5 exposure levels


```{r}

#### for each city create a boxplot showing the individual daily PM2.5 exposure levels for all scenarios

# loop through cities
for (x in 1:length(cities)) {

  n_col <- ncol(io[[cities[x]]]$outcomes$pm_conc_pp)
  
  # extract original scenario names and convert to updated scenario names
  col_names <- names(io[[cities[x]]]$outcomes$pm_conc_pp)[(n_col - scen_length):n_col]
  orig_scen_names <- sub("pm_conc_", "", col_names)
  new_scen_names  <- unlist(lapply(orig_scen_names, FUN=get_qualified_scen_name))
  
  
  # rename columns
  names(io[[cities[x]]]$outcomes$pm_conc_pp)[(n_col - scen_length):n_col] <- new_scen_names
  
  # get PM2.5 individual exposure level data into correct format
  data_long <- gather(io[[cities[x]]]$outcomes$pm_conc_pp, scenario, pm_conc,
                      Baseline:new_scen_names[length(new_scen_names)], factor_key = TRUE)
  
  # create boxplot
  y <- ggplot(data_long, aes(x = scenario, y = pm_conc, fill = scenario)) +
    geom_boxplot(outlier.shape = 8) + ggtitle(cities[x]) + 
    scale_fill_manual("Scenario", values = scen_colours) + 
    labs(y = "Daily PM2.5 exposure levels", x = "Scenarios", title = "") #+
  
  # print to html
  print(y)
  
  #save
  ggsave("figures/ap_pm2.5_dist.svg", plot = y, width=10, height=8)
  
}
```




# Summary statistics of individual PM2.5 exposure levels

```{r, message=FALSE, warning=FALSE, echo=FALSE}

cat(paste0('The change in PM2.5 levels is given as the difference to the reference scenario: ', reference_scenario))


# for each city create a summary table of individual PM2.5 exposure levels giving the mean and the 5th, 50th and 95th percentile levels. Tables also show the PM2.5 concentration levels in the city for each scenario and the changes compared to the reference scenario

data_long <- NA
summary <- NA
for (x in 1:length(cities)) {
 
  n_col <- ncol(io[[cities[x]]]$outcomes$pm_conc_pp)
  
  # rename columns with updated scenario names
  names(io[[cities[x]]]$outcomes$pm_conc_pp)[(n_col - scen_length):n_col] <- new_scen_names
  
  # get data into correct format
  data_long <- gather(io[[cities[x]]]$outcomes$pm_conc_pp, scenario, pm_conc,
                      Baseline:new_scen_names[length(new_scen_names)], factor_key = TRUE)
  
  
  # create summary stats
  summary <- as.data.frame(data_long %>% group_by(scenario) %>%
                             summarise('mean' = mean(pm_conc),
                                       '5th' = quantile(pm_conc, 0.05),
                                       '20th' = quantile(pm_conc, 0.20),
                                       '25th' = quantile(pm_conc, 0.25),
                                       '35th' = quantile(pm_conc, 0.35),
                                       '50th' = quantile(pm_conc, 0.5),
                                       '95th' = quantile(pm_conc, 0.9)) |> mutate_if(is.numeric, round, round_to))
  
  # Extract scenario_pm with two columns with scenario names and scenario_pm_concentrations
  scenario_pm_df <- io[[cities[x]]]$outcomes$scenario_pm |> mutate_if(is.numeric, round, round_to)
  
  # Rename scenario names
  scenario_pm_df$scenario <- unlist(lapply(scenario_pm_df$scenario, FUN=get_qualified_scen_name))
  
  # Join summary and scenario_pm_df based on scenario names
  summary <- left_join(summary, scenario_pm_df) |> mutate(change_PM = round(conc_pm - conc_pm[scenario == "Baseline"], round_to))
  
  # print to html file
  print(kable(summary, caption = cities[x]))
  
}
```


# Summary table of PM 2.5 emission inventories 

```{r, message=FALSE, warning=FALSE, echo=FALSE}

# Create a single table detailing the Baseline PM2.5 emissions for each mode, the city wide PM2.5 concentration levels and the percentage of these emissions attributed to transport for all cities


sl <- list()
for (x in 1:length(cities)){ # loop through cities
  print(cities[x])
  
  # find the modes given in the PM emission inventory for that city
  modes <- names(unlist(io[[cities[x]]]$PM_emission_inventory))
  
  # extract the PM emissions for each mode
  emissions <- as.data.frame(unlist(io[[cities[x]]]$PM_emission_inventory))
  
  # combine modes and emissions into one dataframe
  city_emissions <- cbind(as.data.frame(modes),  as.data.frame(emissions$`unlist(io[[cities[x]]]$PM_emission_inventory)`))
  names(city_emissions)[2] <- "emissions"
  
  # define modes of interest
  select <- c("car", "motorcycle", "bus_driver", "truck", "heavy_truck")
  city_emissions$modes <- as.character(city_emissions$modes)
  
  # call all other modes not in list of modes of interest 'other'
  city_emissions$modes[!(city_emissions$modes %in% select)] <- "other"
  
  # calculate the sum of PM emissions by mode (primarily summing across all newly classified 'other' modes)
  summary <- city_emissions %>% group_by(modes) %>% summarise(sum(emissions))
  names(summary)[2] <- cities[x]
  
  # calculate the percentages of PM emissions attributed to each mode
  summary[[cities[x]]] <- round(summary[[cities[x]]]*100/sum(summary[[cities[x]]]), digits = round_to)
  summary <- as.data.frame(summary)
  
  # rename mode columns including the word percentage
  summary$modes <- paste0(summary$modes, ' (percentage)')
  
  # add transport share 
  summary[nrow(summary) + 1,1] <- "Transport share (percentage)"
  summary[nrow(summary),2] <- as.character(round(pm_trans_share[[cities[x]]] * 100, digits = round_to))
  
  # add city wide PM2.5 concentration levels
  summary[nrow(summary) + 1,1] <- "PM2.5 Concentration"
  summary[nrow(summary),2] <- as.character(pm_conc_base[[cities[x]]])
  
  # add to io list
  io[[cities[x]]]$summary_emission <- summary
  
  # create one dataframe containing all cities
  if (length(sl) == 0){
    sl <- summary
  }else{
    sl <- left_join(sl , summary)
  }
  
}

# print table to html
print(kable(sl))
```


# Summary table of total CO2 emissions related to transport in each scenario

```{r, message=FALSE, warning=FALSE, echo=FALSE}

# create summary table of CO2 emissions in each scenario
co2_emission_inventory <- list()
td <- NA

for (city in cities) { # loop through cities
  
  # extract CO2 emissions
  td <- round(colSums(io[[city]]$outcomes$co2_emission_inventory, na.rm = T), round_to) %>% 
    as.data.frame() %>% tibble::rownames_to_column()
  names(td) <- c('Scenario', city)
  
  # create one dataframe containing all cities
  if (length(co2_emission_inventory) == 0)
    co2_emission_inventory <- td
  else
    co2_emission_inventory <- left_join(co2_emission_inventory, td)
  
}

# Dan: here the order is different (bus before car)
# co2_emission_inventory$Scenario <- new_scen_names
co2_emission_inventory$Scenario <- sapply(co2_emission_inventory$Scenario, FUN = get_qualified_scen_name)

bv <- co2_emission_inventory |> filter(Scenario == "Baseline") |> dplyr::select(city) |> pull()

pop_size <- sum(io[[city]]$demographic$population)

co2_emission_inventory <- co2_emission_inventory |> mutate(change_baseline = !!rlang::sym(city) - bv, change_CO2_percentage = ifelse(change_baseline == 0, 0, round(change_baseline/bv * 100, round_to)),
                                                           CO2_per_capita = round(!!rlang::sym(city)/pop_size, round_to))

# print to html
print(kable(co2_emission_inventory))

```



# Boxplots of individual physical activity (MMETs) levels

```{r, message=FALSE, warning=FALSE, echo=FALSE}
# create boxplots for each city showing the individual mMET levels for each scenario

limit = 100

for (x in 1:length(cities)) { # loop through cities
  
  n_col <- ncol(io[[cities[x]]]$outcomes$mmets) # define columns of interests
  change_names <- which(grepl("_mmet", names(io[[cities[x]]]$outcomes$mmets), fixed = TRUE))
  names(io[[cities[x]]]$outcomes$mmets)[change_names] <- sapply(gsub("_mmet" , "", names(io[[cities[x]]]$outcomes$mmets)[change_names]), FUN = get_qualified_scen_name)
  
  data_long <- pivot_longer(io[[cities[x]]]$outcomes$mmets |> dplyr::select(participant_id, new_scen_names), cols = !participant_id, names_to = "scenario", values_to = "mmet")
  
  # create the boxplots
  y <- ggplot(data_long, aes(x = scenario, y = mmet, fill = scenario)) +
    geom_boxplot(outlier.shape = NA) + ggtitle(cities[x]) + 
    scale_fill_manual("Scenario", values = scen_colours) + 
    labs(y = "mMET-hours/week", x = "Scenarios", title = "")+  ylim(0, limit)
  
  # print to html
  print(y)
  
  ggsave("figures/pa_distr.svg", plot = y, width=10, height=8)
  
}
```


# Summary statistics of individual physical activity levels (mMET-hours/week)

```{r, message=FALSE, warning=FALSE, echo=FALSE}

# create one table for each city giving the mean, 5th, 50th and 95th percentile levels of individual physical activity levels (mMETs) for each scenario

for (x in 1:length(cities)) { # loop through the cities
  
  n_col <- ncol(io[[cities[x]]]$outcomes$mmets) # find the number of columns
  # names(io[[cities[x]]]$outcomes$mmets)[(n_col - scen_length):n_col] <- new_scen_names # assign new column names
  change_names <- which(grepl("_mmet", names(io[[cities[x]]]$outcomes$mmets), fixed = TRUE))
  names(io[[cities[x]]]$outcomes$mmets)[change_names] <- sapply(gsub("_mmet" , "", names(io[[cities[x]]]$outcomes$mmets)[change_names]), FUN = get_qualified_scen_name)
  
  # create dataframe with individual mMET values
  data_long <- pivot_longer(io[[cities[x]]]$outcomes$mmets |> dplyr::select(participant_id, new_scen_names), cols = !participant_id, names_to = "Scenario", values_to = "mmet")
  
  # create summary stats
  summary <- as.data.frame(data_long %>% group_by(Scenario) %>% 
                             summarise('mean' = mean(mmet),
                                       '5th' = quantile(mmet, 0.05),
                                       '20th' = quantile(mmet, 0.20),
                                       '25th' = quantile(mmet, 0.25),
                                       '35th' = quantile(mmet, 0.35),
                                       '50th' = quantile(mmet, 0.5),
                                       '95th' = quantile(mmet, 0.9)))
  summary <- cbind(summary$Scenario ,round(summary[,-1], digits = round_to))
  names(summary)[1] <- "Scenario"
 
  # print to html
  print(kable(summary, caption = cities[x]))

}
```


## Comparison of PA volume of baseline and bus scenario

```{r, message=FALSE, warning=FALSE, echo=FALSE}

for (x in 1:length(cities)) {
  
  mmets <- io[[cities[x]]]$outcomes$mmets #|> pivot_longer(cols = ends_with("mmet"))
  
  change_names <- which(grepl("_mmet", names(mmets), fixed = TRUE))
  names(mmets)[change_names] <- sapply(gsub("_mmet" , "", names(mmets)[change_names]), FUN = get_qualified_scen_name)
  
  mmets <- mmets |> pivot_longer(cols = -c(1:4)) |> rename(Scenario = name)
  
  mmets_df <- mmets |> filter(Scenario %in% c("Baseline", "Bus"))
  
  y <- ggplot(mmets_df, aes(x=value, colour=Scenario)) + 
                     geom_density() + 
                     scale_color_manual(values = scen_colours) + 
                     xlim(0, 30) +
                     geom_vline(xintercept = 17.5, linetype="dashed", color = "red") +
                     labs(title = "",
                          x = "mMET-hours/week per person",
                          y = "Density") +
                    annotate(x = 17.5, y = +Inf, 
                             label = "17.5 mMET-hours/week", 
                             vjust = 2, geom="label")
  
  # print to html
  print(y)
  
  # ggsave
  ggsave("figures/pa_vol_base_bus.svg", plot = y, width=10, height=8)
}




```



## Comparison of PA volume of baseline and cycling scenario

```{r, message=FALSE, warning=FALSE, echo=FALSE}

for (x in 1:length(cities)) {
  
  mmets <- io[[cities[x]]]$outcomes$mmets #|> pivot_longer(cols = ends_with("mmet"))
  
  change_names <- which(grepl("_mmet", names(mmets), fixed = TRUE))
  names(mmets)[change_names] <- sapply(gsub("_mmet" , "", names(mmets)[change_names]), FUN = get_qualified_scen_name)
  
  mmets <- mmets |> pivot_longer(cols = -c(1:4)) |> rename(Scenario = name)
  
  mmets_df <- mmets |> filter(Scenario %in% c("Baseline", "Cycling"))
  
  y <- ggplot(mmets_df, aes(x=value, colour=Scenario)) + 
                     geom_density() + 
                     scale_color_manual(values = scen_colours) + 
                     xlim(0, 30) +
                     geom_vline(xintercept = 17.5, linetype="dashed", color = "red") +
                     labs(title = "",
                          x = "mMET-hours/week per person",
                          y = "Density") +
    annotate(x = 17.5, y = +Inf, label = "17.5 mMET-hours/week", vjust = 2, geom="label")
  
  # print to html
  print(y)
  
  ggsave("figures/pa_vol_base_cyc.svg", plot = y, width=10, height=8)
}




```



## Deciles of mMET-hours/week
```{r}


l <- htmltools::tagList()

for (x in 1:length(cities)) {
  
  mmets <- io[[cities[x]]]$outcomes$mmets #|> pivot_longer(cols = ends_with("mmet"))
  
  change_names <- which(grepl("_mmet", names(mmets), fixed = TRUE))
  names(mmets)[change_names] <- sapply(gsub("_mmet" , "", names(mmets)[change_names]), FUN = get_qualified_scen_name)
  
  mmets <- mmets |> pivot_longer(cols = -c(1:4)) |> rename(Scenario = name)


df_deciles <- mmets  |> 
  group_by(Scenario) |> 
  summarise(q = list(quantile(value, probs = seq(0, 0.9, by = 0.1) ))) |> 
  unnest_wider(q) |> 
  pivot_longer(cols = contains("%"), names_to = "decile", values_to = "value")


df_deciles_n <- mmets  |> 
  group_by(Scenario) |> 
  summarise(q = list(quantile(value, probs = c(0.05, 0.20, 0.25, 0.35, 0.5, 0.9) ))) |> 
  unnest_wider(q) |> 
  pivot_longer(cols = contains("%"), names_to = "decile", values_to = "value") |> 
  pivot_wider(names_from = decile, values_from = value)

l# Plot deciles by scenario
y <- ggplot(df_deciles, aes(x = decile, y = value, color = Scenario)) +
  geom_line(aes(group = Scenario)) +
  geom_point() +
  labs(title = "", x = "Deciles", y = "mMET-hours/week") +
  geom_hline(yintercept = 17.5, linetype="dashed", color = "red") +
  scale_color_manual(values = scen_colours) + 
  annotate(y = 17.5, x = 2, 
                             label = "17.5 mMET-hours/week", geom="label") +
  scale_x_discrete(labels = paste0("D_", seq(from = 0, to = 9, by = 1)))

  # print to html
  print(y)
  
  ggsave("figures/pa_deciles.svg", plot = y, width=10, height=8)
  
  # l[[i]] <- as_widget(plotly::ggplotly(y) %>%
  # config(
  #   toImageButtonOptions = list(
  #               format = "svg",
  #               filename = "PA-volume-deciles.svg",
  #               width = NULL,
  #               height = NULL
  # )))


}

# l

```

