---
title: "Summary Tables ITHIMR"
author: "Rahul Goel, MRC Epidemiology Unit, University of Cambridge, UK"
date: "25 April 2019"
output:
  html_document: default
  word_document: default
  pdf_document: default
---


# Introduction
These are the summary tables of the following items
1) Individual-level PM2.5 concentrations for baseline and scenarios
2) Individual-level physical activity for baseline and scenarios
3) Distance mode shares for baseline and scenarios


```{r, echo=FALSE}
#setwd('C:/Users/rg574/Dropbox/spatiotemporal analysis fatalities inida/Rajasthan tourism road deaths') #to create pretty tables
```

```{r, message=FALSE, warning=FALSE}
#library(INLA)     #loading the INLA package
library(ggplot2)  #loading ggplot package for plotting graphs
library(knitr)     
library(tidyr)
library(dplyr)
library(kableExtra)

```


# Boxplots of Individual-level PM2.5 Concentrations

```{r, message=FALSE, warning=FALSE, echo=FALSE}
io <- readRDS("results/multi_city/io.rds")

cities<- names(io)
cities<- cities[-c(1,2)]

for (x in 1: length(cities))
{
  names(io[[cities[x]]]$outcomes$pm_conc_pp)[6:11]<-c("baseline","walk_scen", "bike_scen", "car_scen", "MC_scen", "bus_scen")
  data_long <- gather(io[[cities[x]]]$outcomes$pm_conc_pp, scenario, pm_conc, baseline:bus_scen, factor_key=TRUE)
  x<-ggplot(data_long, aes(x=scenario, y=pm_conc, fill=scenario)) + geom_boxplot()+ ggtitle(cities[x])+ labs(y="Daily PM2.5 Concentration", x = "Scenarios")
  print(x)
  
}
```




# Descriptive tables of Individual-level PM2.5 Concentrations

```{r, message=FALSE, warning=FALSE, echo=FALSE}

for (x in 1: length(cities))
{
  names(io[[cities[x]]]$outcomes$pm_conc_pp)[6:11]<-c("baseline","walk_scen", "bike_scen", "car_scen", "MC_scen", "bus_scen")
  data_long <- gather(io[[cities[x]]]$outcomes$pm_conc_pp, scenario, pm_conc, baseline:bus_scen, factor_key=TRUE)
  summary<- as.data.frame(data_long %>% group_by(scenario) %>% summarise('mean'=mean(pm_conc),'5th'=quantile(pm_conc, 0.05),'50th'=quantile(pm_conc, 0.5),'95th'=quantile(pm_conc, 0.9)))
  summary<- cbind(summary$scenario ,round(summary[,2:5], digits=1))
  names(summary)[1]<-"Scenario"
  print (as.character(cities[x]))
  print(summary)
  
  summary %>%
  kable() %>%
  kable_styling()
  
}
```




# Descriptive tables of emission inventory

```{r, message=FALSE, warning=FALSE, echo=FALSE}

city<-cities
trans_share<-c(22.5, 40.0, 22.5, 28.1) 
pm_conc<- c(50, 18, 122, 47 )
shares<- as.data.frame(cbind(city,as.numeric(trans_share), pm_conc))
names(shares)[2]<- "trans_share"
for (x in 1:length(cities))
{
  modes<-names(unlist(io[[cities[x]]]$emission_inventory))
  emissions<-as.data.frame(unlist(io[[cities[x]]]$emission_inventory))
  city_emissions<-cbind(as.data.frame(modes),  as.data.frame(emissions$`unlist(io[[cities[x]]]$emission_inventory)`))
  names(city_emissions)[2]<- "emissions"
  select<- c("car", "motorcycle", "bus_driver", "truck", "big_truck")
  city_emissions$modes<- as.character(city_emissions$modes)
  city_emissions$modes[!(city_emissions$modes %in% select)]<- "other"
  summary<-city_emissions %>% group_by(modes) %>% summarise(sum(emissions))
  names(summary)[2]<- "emissions"
  summary$emissions <- round(summary$emissions*100/sum(summary$emissions), digits=1)
  print (as.character(cities[x]))
  summary(as.data.frame(summary))
  summary[nrow(summary)+1,1]<-"Transport share"
  summary[nrow(summary),2]<-as.character(shares$trans_share[x])
  summary[nrow(summary)+1,1]<-"PM2.5 Conc"
  summary[nrow(summary),2]<-as.character(shares$pm_conc[x])
  print (summary)
  
}

```



# Boxplots of Individual-level Physical activity (MMETs)

```{r, message=FALSE, warning=FALSE, echo=FALSE}


for (x in 1: length(cities))
{
  names(io[[cities[x]]]$outcomes$mmets)[5:10]<-c("baseline","walk_scen", "bike_scen", "car_scen", "MC_scen", "bus_scen")
  data_long <- gather(io[[cities[x]]]$outcomes$mmets, scenario, mmet, baseline:bus_scen, factor_key=TRUE)
  x<-ggplot(data_long, aes(x=scenario, y=mmet, fill=scenario)) + geom_boxplot()+ ggtitle(cities[x])+ labs(y="Weekly MMET", x = "Scenarios")
  print(x)
  
}
```

# Descriptive tables of Individual-level Physical activity (MMETs)

```{r, message=FALSE, warning=FALSE, echo=FALSE}

for (x in 1: length(cities))
{
  names(io[[cities[x]]]$outcomes$mmets)[5:10]<-c("baseline","walk_scen", "bike_scen", "car_scen", "MC_scen", "bus_scen")
  data_long <- gather(io[[cities[x]]]$outcomes$mmets, scenario, mmet, baseline:bus_scen, factor_key=TRUE)
  summary<- as.data.frame(data_long %>% group_by(scenario) %>% summarise('mean'=mean(mmet),'5th'=quantile(mmet, 0.05),'50th'=quantile(mmet, 0.5),'95th'=quantile(mmet, 0.9)))
  summary<- cbind(summary$scenario ,round(summary[,2:5], digits=1))
  names(summary)[1]<-"Scenario"
  print (as.character(cities[x]))
  print(summary)
  

  
}
```

# Descriptive tables of injury outcomes

```{r, message=FALSE, warning=FALSE, echo=FALSE}

for (x in 1: length(cities))
{

  summary<- as.data.frame(io[[cities[x]]]$outcomes$injuries %>% group_by(scenario) %>% summarise('Ped'=sum(pedestrian,na.rm=T),'Bike'= sum(bicycle), 'Car'=sum(car), "Motorcycle"=sum(motorcycle,na.rm=T), "All modes"=sum(Deaths,na.rm=T)))
  summary$scenario<- c("baseline","walk_scen", "bike_scen", "car_scen", "MC_scen", "bus_scen")
  summary<- cbind(summary$scenario ,round(summary[,2:6], digits=0))
  names(summary)[1]<-"Scenario"
  print (as.character(cities[x]))
  print(summary)

}
```

# Striking vehicles in scenarios

```{r, message=FALSE, warning=FALSE, echo=FALSE}

for (x in 1: length(cities))
{

scenarios<- c('Baseline', 'Scenario 1', 'Scenario 2', 'Scenario 3', 'Scenario 4', 'Scenario 5')
for (i in 1: length(scenarios))
{
whw<-as.data.frame(rowSums(io[[cities[x]]]$outcomes$whw[[scenarios[i]]]$whw))
noov<-as.data.frame(rowSums(io[[cities[x]]]$outcomes$whw[[scenarios[i]]]$noov))
names(whw)[1]<- as.character(scenarios[i])
names(noov)[1]<-as.character(scenarios[i])

if (i ==1 )
{
 summary<-round(rbind(whw,noov), digits = 1)
} 
else
{
summary<- cbind(summary, round(rbind(whw, noov), digits=1) ) 
}

}

print (as.character(cities[x]))
print(summary)

}

```



# Distance share by scenarios in percentages (excludes city-specific minority modes-- auto rickshaws, subway, etc.)

```{r, message=FALSE, warning=FALSE, echo=FALSE}
for (x in 1: length(cities))
{
  
  select<- c("car", "motorcycle", "walking", "bicycle", "bus")
  
  io[[cities[x]]]$trip_scen_sets$trip_mode[!io[[cities[x]]]$trip_scen_sets$trip_mode %in% select]<- "other"
  
  dist_scen<- io[[cities[x]]]$trip_scen_sets %>% group_by(trip_mode, scenario) %>% summarise(sum(trip_distance))
  dist_scen<- as.data.frame (dist_scen)
  names(dist_scen)[3]<-"distance"
  dist_scen$distance<- round(dist_scen$distance, digits=0)
    dist_scen<-spread(dist_scen, trip_mode, distance)
  dist_scen$sum<-rowSums (dist_scen[2:(ncol(dist_scen))], na.rm = FALSE, dims = 1)
  dist_scen_prop<- round(dist_scen[,2:(ncol(dist_scen))]*100/dist_scen$sum, digits=1)
  dist_scen_prop<- cbind(dist_scen[,1], dist_scen_prop)
  
  names(dist_scen_prop)[1]<-"Scenario"
  dist_scen_prop$Scenario<- c("baseline","walk_scen", "bike_scen", "car_scen", "MC_scen", "bus_scen")
  print (as.character(cities[x]))
  print(dist_scen_prop)
  print(dist_scen)
  #library(knitr)
  #library(kableExtra)
  #kable(dist_scen_prop)
}
```
