---
title: "Summary Tables"
output: html_document
---

```{r setup, include=FALSE}
library(knitr)
library(pracma)
library(summarytools)
library(dplyr)
knitr::opts_chunk$set(comment=NA, prompt=FALSE, cache=FALSE, echo=F, results='asis')

```


```{r loadLibraries, echo = F, message = F}

st_options(bootstrap.css     = FALSE,       # Already part of the theme so no need for it
           plain.ascii       = FALSE,       # One of the essential settings
           style             = "rmarkdown", # Idem.
           dfSummary.silent  = TRUE,        # Suppresses messages about temporary files
           footnote          = NA,          # Keeping the results minimalistic
           subtitle.emphasis = FALSE)       # For the vignette theme, this gives
                                            # much better results. Your mileage may vary

```

```{r load_objects = "asis"}
io <- readRDS("results/multi_city/io.rds")
# Assumes that multi_city_script.R has been run till 
cities <- c('accra','sao_paulo','delhi','bangalore')

# round to
round_to <- 1

# Set plot_mmets to F
plot_mmets <- F

```

```{r preprocessing}
collapse_ages <- function(data,ages=c('15-49','50-69'),age_lab='age_cat'){
  target_min_age <- as.numeric(sapply(ages,function(x)strsplit(x,'-')[[1]][1]))
  target_max_age <- as.numeric(sapply(ages,function(x)strsplit(x,'-')[[1]][2]))
  min_ages <- as.numeric(sapply(data[[age_lab]],function(x)strsplit(x,'-')[[1]][1]))
  max_ages <- as.numeric(sapply(data[[age_lab]],function(x)strsplit(x,'-')[[1]][2]))
  genders <- unique(data$sex)
  if(ncol(data)>3) {
    reformatted <- do.call(rbind,lapply(1:length(ages),
    function(x) t(sapply(genders,
          function(y) 
            if(ncol(data)>3) colSums(data[min_ages<=target_max_age[x]&max_ages>=target_min_age[x]&data$sex==y,-c(1,2),drop=F])
          else sum(data[min_ages<=target_max_age[x]&max_ages>=target_min_age[x]&data$sex==y,-c(1,2),drop=F])
         ))
  ))
  data.frame(age_cat=rep(ages,each=2),sex=rep(genders,2),reformatted,stringsAsFactors=F)
  }else{
  reformatted <- do.call(c,lapply(1:length(ages),
    function(x) sapply(genders,
          function(y) 
            sum(data[min_ages<=target_max_age[x]&max_ages>=target_min_age[x]&data$sex==y,-c(1,2),drop=F])
         )
  ))
  data.frame(age=rep(ages,each=2),sex=rep(genders,2),population=as.numeric(reformatted),stringsAsFactors=F)
  }
}

scen_prop <- io$scen_prop
io <- io[-2]
for(i in 1:length(io)) {
  io[[i]]$demographic$age[io[[i]]$demographic$age=='5-9'] <- '05-9'
  io[[i]]$outcomes$hb$deaths$age_cat[io[[i]]$outcomes$hb$deaths$age_cat=='5-9'] <- '05-9'
  io[[i]]$outcomes$hb$ylls$age_cat[io[[i]]$outcomes$hb$ylls$age_cat=='5-9'] <- '05-9'
  io[[i]]$outcomes$pathway_hb$deaths$age_cat[io[[i]]$outcomes$pathway_hb$deaths$age_cat=='5-9'] <- '05-9'
  io[[i]]$outcomes$pathway_hb$ylls$age_cat[io[[i]]$outcomes$pathway_hb$ylls$age_cat=='5-9'] <- '05-9'
  io[[i]]$outcomes$hb$deaths <- io[[i]]$outcomes$hb$deaths[,!sapply(names(io[[i]]$outcomes$hb$deaths),function(x)grepl('ac|neo',as.character(x)))]
  io[[i]]$outcomes$hb$ylls <- io[[i]]$outcomes$hb$ylls[,!sapply(names(io[[i]]$outcomes$hb$ylls),function(x)grepl('ac|neo',as.character(x)))]
  io[[i]]$outcomes$pathway_hb$deaths <- io[[i]]$outcomes$pathway_hb$deaths[,!sapply(names(io[[i]]$outcomes$pathway_hb$deaths),function(x)grepl('ac|neo',as.character(x)))]
  io[[i]]$outcomes$pathway_hb$ylls <- io[[i]]$outcomes$pathway_hb$ylls[,!sapply(names(io[[i]]$outcomes$pathway_hb$ylls),function(x)grepl('ac|neo',as.character(x)))]
}
for(city in cities)
  for(type in c('hb','pathway_hb'))
    for(out in c('deaths','ylls'))
      io[[city]]$outcomes[[type]][[out]] <- collapse_ages(io[[city]]$outcomes[[type]][[out]])
for(city in cities) io[[city]]$demographic <- collapse_ages(io[[city]]$demographic,age_lab='age')
pop_by_age <- lapply(io,function(x)sapply(unique(x$demographic$age),function(y)sum(subset(x$demographic,age==y)$population)))
pop_by_gender <- lapply(io,function(x)sapply(unique(x$demographic$sex),function(y)sum(subset(x$demographic,sex==y)$population)))
injury_col <- which(colnames(io$accra$outcomes$hb$deaths)=='scen1_deaths_inj')
ap_cols <- which(sapply(colnames(io$accra$outcomes$pathway_hb$deaths),function(x)grepl('ap',as.character(x))))
pa_cols <- which(sapply(colnames(io$accra$outcomes$pathway_hb$deaths),function(x)grepl('pa',as.character(x))))
scen_names <- rownames(scen_prop)

```


## TOTAL

Change in deaths total (for the city based on real population size) by age group by scenario

```{r scen_prop = "asis"}
death_totals <- lapply(io,function(x){
  temp <- sapply(1:5,function(y){
    xx <- x$outcomes$hb$deaths
    xxx <- rowSums(xx[,seq(2+y,ncol(xx),by=5)])
    sapply(sort(unique(xx$age_cat)),function(z)
      sum(xxx[xx$age_cat==z]))
  })
  #rownames(temp) <- apply(x$outcomes$hb$deaths[,1:2],1,function(z)paste0(z[1],'_',z[2]))
  colnames(temp) <- scen_names
  temp
  })

death_totals_rounded <- lapply(death_totals, function(x)round(x,round_to))

death_totals_rounded <- lapply(death_totals_rounded,function(x)rbind(x,Total=colSums(x)))


for(city in cities) {
  print(kable(death_totals_rounded[[city]], caption = paste("Change in deaths total in ", city)))
  cat("\n")
}
```

Change in deaths per 100,000 people by age group by scenario

```{r scen_prop = "asis"}
death_rates <- lapply(cities,function(x) death_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000)
names(death_rates) <- cities

death_rates_rounded <- lapply(death_rates, function(x)round(x,round_to))

death_rates_rounded <- lapply(death_rates_rounded,function(x)rbind(x,Total=colSums(x)))

for(city in cities) {
  print(kable(death_rates_rounded[[city]], caption = paste("Change in deaths per 100,000 in ", city)))
  cat("\n")
}
```

YLLs total (for the city based on real population size) by age group  by scenario

```{r scen_prop = "asis"}
yll_totals <- lapply(io,function(x){
  temp <- sapply(1:5,function(y){
    xx <- x$outcomes$hb$ylls
    xxx <- rowSums(xx[,seq(2+y,ncol(xx),by=5)])
    sapply(sort(unique(xx$age_cat)),function(z)
      sum(xxx[xx$age_cat==z]))
  })
  colnames(temp) <- scen_names
  temp
  })
yll_totals_rounded <- lapply(yll_totals,function(x)rbind(x,Total=colSums(x)))
yll_totals_rounded <- lapply(yll_totals_rounded, function(x)round(x,round_to))


for(city in cities) {
  print(kable(yll_totals_rounded[[city]], caption = paste("Change in YLL total in ", city)))
  cat("\n")
}
```

YLLs per 100,000 people by age group by scenario

```{r scen_prop = "asis"}
yll_rates <- lapply(cities,function(x) yll_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000)
names(yll_rates) <- cities
yll_rates_rounded <- lapply(yll_rates,function(x)rbind(x,Total=colSums(x)))
yll_rates_rounded <- lapply(yll_rates_rounded, function(x)round(x,round_to))


for(city in cities) {
  print(kable(yll_rates_rounded[[city]], caption = paste("Change in YLLs per 100,000 in ", city)))
  cat("\n")
}
```

YLLs per 100,000 people by gender by age group scenario

```{r scen_prop = "asis"}
yll_totals <- lapply(io,function(x){
  temp <- sapply(1:5,function(y){
    xx <- x$outcomes$hb$ylls
    rowSums(xx[,seq(2+y,ncol(xx),by=5)])
  })
  rownames(temp) <- apply(x$outcomes$hb$deaths[,1:2],1,function(z)paste0(z[1],'_',z[2]))
  colnames(temp) <- scen_names
  temp
  })

yll_rates <- lapply(cities,function(x) 
  yll_totals[[x]][match(apply(io[[x]]$demographic[,c('sex','age')],1,function(z)paste0(z[2],'_',z[1])),rownames(yll_totals[[x]])),]/
    t(repmat(io[[x]]$demographic$population,5,1))*100000)
names(yll_rates) <- cities
yll_rates_rounded <- lapply(yll_rates,function(x)rbind(x,Total=colSums(x)))
yll_rates_rounded <- lapply(yll_rates_rounded, function(x)round(x,round_to))


for(city in cities) {
  print(kable(yll_rates_rounded[[city]], caption = paste("Change in YLLs per 100,000 in ", city)))
  cat("\n")
}
``` 

 
## BY PATHWAY

By pathway (with non- injury separate & summed)

Change in deaths total (for the city based on real population size) by age group by scenario

```{r}
injury_totals <- lapply(io,function(x){
  xx <- x$outcomes$hb$deaths
  xxx <- sapply(1:5,function(y)sapply(sort(unique(xx$age_cat)),function(z)sum(xx[xx$age_cat==z,injury_col-1+y])))
  colnames(xxx) <- scen_names
  xxx
  })
injury_totals_rounded <- lapply(injury_totals,function(x)rbind(x,Total=colSums(x)))
injury_totals_rounded <- lapply(injury_totals_rounded, function(x)round(x,round_to))

for(city in cities) {
  print(kable(injury_totals_rounded[[city]], caption = paste("Change in deaths due to injury in ", city)))
  cat("\n")
}

pa_totals <- lapply(io,function(x){
  xx <- x$outcomes$pathway_hb$deaths
  xxx <- sapply(1:5,function(y){
    xxx <- rowSums(xx[,pa_cols[seq(y,length(pa_cols),by=5)]])
    sapply(sort(unique(xx$age_cat)),function(z)sum(xxx[xx$age_cat==z]))
  })
  colnames(xxx) <- scen_names
  xxx
  })
pa_totals_rounded <- lapply(pa_totals,function(x)rbind(x,Total=colSums(x)))
pa_totals_rounded <- lapply(pa_totals_rounded, function(x)round(x,round_to))

for(city in cities) {
  print(kable(pa_totals_rounded[[city]], caption = paste("Change in deaths due to PA in ", city)))
  cat("\n")
}

ap_totals <- lapply(io,function(x){
  xx <- x$outcomes$pathway_hb$deaths
  xxx <- sapply(1:5,function(y){
    xxx <- rowSums(xx[,ap_cols[seq(y,length(ap_cols),by=5)]])
    sapply(sort(unique(xx$age_cat)),function(z)sum(xxx[xx$age_cat==z]))
  })
  colnames(xxx) <- scen_names
  xxx
  })
ap_totals_rounded <- lapply(ap_totals,function(x)rbind(x,Total=colSums(x)))
ap_totals_rounded <- lapply(ap_totals_rounded, function(x)round(x,round_to))

for(city in cities) {
  print(kable(ap_totals_rounded[[city]], caption = paste("Change in deaths due to AP in ", city)))
  cat("\n")
}
```

Change in deaths per 100,000 people by age group by scenario

```{r scen_prop = "asis"}
injury_rates <- lapply(cities,function(x) injury_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000)
names(injury_rates) <- cities
injury_rates_rounded <- lapply(injury_rates,function(x)rbind(x,Total=colSums(x)))
injury_rates_rounded <- lapply(injury_rates_rounded, function(x)round(x,round_to))


for(city in cities) {
  print(kable(injury_rates_rounded[[city]], caption = paste("Change in deaths due to injury per 100,000 in ", city)))
  cat("\n")
}
```

YLLs total (for the city based on real population size) by age group by scenario

```{r}
injury_totals <- lapply(io,function(x){
  xx <- x$outcomes$hb$ylls
  xxx <- sapply(1:5,function(y)sapply(sort(unique(xx$age_cat)),function(z)sum(xx[xx$age_cat==z,injury_col-1+y])))
  colnames(xxx) <- scen_names
  xxx
  })
injury_totals_rounded <- lapply(injury_totals,function(x)rbind(x,Total=colSums(x)))
injury_totals_rounded <- lapply(injury_totals_rounded, function(x)round(x,round_to))

for(city in cities) {
  print(kable(injury_totals_rounded[[city]], caption = paste("Change in YLLs due to injury in ", city)))
  cat("\n")
}
```

YLLs per 100,000 people by age group by scenario

```{r scen_prop = "asis"}
injury_rates <- lapply(cities,function(x) injury_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000)
names(injury_rates) <- cities
injury_rates_rounded <- lapply(injury_rates,function(x)rbind(x,Total=colSums(x)))
injury_rates_rounded <- lapply(injury_rates_rounded, function(x)round(x,round_to))


for(city in cities) {
  print(kable(injury_rates_rounded[[city]], caption = paste("Change in YLLs due to injury per 100,000 in ", city)))
  cat("\n")
}
```

## BY DISEASE

Change in deaths total (for the city based on real population size) by scenario

```{r}

disease_totals <- lapply(io,function(x){
  xx <- x$outcomes$hb$deaths
  xxx <- sapply(1:5,function(y){
    colSums(xx[,seq(y+2,ncol(xx),by=5)])
  })
  colnames(xxx) <- scen_names
  rownames(xxx) <- sapply(rownames(xxx),function(y)gsub('scen1_','',y))
  xxx
  })
disease_totals_rounded <- lapply(disease_totals,function(x)rbind(x,Total=colSums(x)))
disease_totals_rounded <- lapply(disease_totals_rounded, function(x)round(x,round_to))

for(city in cities) {
  print(kable(disease_totals_rounded[[city]], caption = paste("Change in deaths due to disease in ", city)))
  cat("\n")
}


```

Change in deaths per 100,000 people by scenario

```{r scen_prop = "asis"}
disease_rates <- lapply(cities,function(x) disease_totals[[x]]/sum(pop_by_age[[x]])*100000)
names(disease_rates) <- cities
disease_rates_rounded <- lapply(disease_rates,function(x)rbind(x,Total=colSums(x)))
disease_rates_rounded <- lapply(disease_rates_rounded, function(x)round(x,round_to))


for(city in cities) {
  print(kable(disease_rates_rounded[[city]], caption = paste("Change in deaths due to disease per 100,000 in ", city)))
  cat("\n")
}
```

Change in YLL total (for the city based on real population size) by scenario

```{r}

disease_totals <- lapply(io,function(x){
  xx <- x$outcomes$hb$ylls
  xxx <- sapply(1:5,function(y){
    colSums(xx[,seq(y+2,ncol(xx),by=5)])
  })
  colnames(xxx) <- scen_names
  rownames(xxx) <- sapply(rownames(xxx),function(y)gsub('scen1_','',y))
  xxx
  })
disease_totals_rounded <- lapply(disease_totals,function(x)rbind(x,Total=colSums(x)))
disease_totals_rounded <- lapply(disease_totals_rounded, function(x)round(x,round_to))

for(city in cities) {
  print(kable(disease_totals_rounded[[city]], caption = paste("Change in YLL due to disease in ", city)))
  cat("\n")
}


```

Change in YLL per 100,000 people by scenario

```{r scen_prop = "asis"}
disease_rates <- lapply(cities,function(x) disease_totals[[x]]/sum(pop_by_age[[x]])*100000)
names(disease_rates) <- cities
disease_rates_rounded <- lapply(disease_rates,function(x)rbind(x,Total=colSums(x)))
disease_rates_rounded <- lapply(disease_rates_rounded, function(x)round(x,round_to))


for(city in cities) {
  print(kable(disease_rates_rounded[[city]], caption = paste("Change in YLL due to disease per 100,000 in ", city)))
  cat("\n")
}
```
