---
title: "Summary Tables"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment=NA, prompt=FALSE, cache=FALSE, echo=F, results='asis', warning = F, message = F)

```

```{r helper_functions, echo = F, message = F}

# Source: https://stackoverflow.com/questions/28159936/formatting-large-currency-or-dollar-values-to-millions-billions
comprss <- function(tx) { 
  div <- findInterval(as.numeric(gsub("\\,", "", tx)), 
                      c(0, 1e3, 1e6, 1e9, 1e12) )  # modify this if negative numbers are possible
  paste(round( as.numeric(gsub("\\,","",tx))/10^(3*(div-1)), 2), 
        c("","K","M","B","T")[div] )
}

```

```{r loadLibraries, echo = F, message = F}
suppressWarnings({

library(summarytools)
library(knitr)
library(summarytools)
library(tidyverse)
library(gt)
library(pracma)
library(data.table)
library(writexl)
})

options(dplyr.summarise.inform = FALSE)

st_options(bootstrap.css     = FALSE,       # Already part of the theme so no need for it
           plain.ascii       = FALSE,       # One of the essential settings
           style             = "rmarkdown", # Idem.
           dfSummary.silent  = TRUE,        # Suppresses messages about temporary files
           footnote          = NA,          # Keeping the results minimalistic
           subtitle.emphasis = FALSE)       # For the vignette theme, this gives
                                            # much better results. Your mileage may vary

```

```{r load_objects = "asis", echo = F, message = F}
io <- readRDS("results/multi_city/io.rds")
# Assumes that multi_city_script.R has been run till 
# Get names of cities from the io object
cities <<- names(io)[!names(io) %in% 'scen_prop']
LATAM <<- F
AFRICA_INDIA <<- F
NSCEN <- nrow(io$scen_prop)
#cities <- c('accra','sao_paulo','buenos_aires')

# cities <- c('sao_paulo')

# Read trip_order
trip_order <- read_csv("data/global/trips/mode_order.csv")

# round to
round_to <- 1

# Set plot_mmets to F
plot_mmets <- F

```
# **1st option**
## Scenario definition 
Table displays highest propensity for each distance category, for a given mode.

Table displays highest propensity (%) for each distance category, for a given mode.

In scenario generation, trips are sampled without replacement to increase the share of the requested mode up to the total shown.

Distance categories are: 

0-2 km = \{trip distance < 2\}

2-6 km = \{2 <= trip distance < 6\}

6+ km = \{6 <= trip distance\}

```{r scen_prop = "asis"}

scen_prop <- round(io$scen_prop, round_to)

#rownames(scen_prop) <- paste(rownames(io$scen_prop), "scen", sep = "_")
rownames(scen_prop) <- paste0(substr(toupper(rownames(io$scen_prop)),1,3),"_SC")

kable(scen_prop, headings = "Scenario Proportions")

```


```{r warning=FALSE, echo=F, message=FALSE}

dat <- list()

for (city in cities) {
  
dat[[city]] <- io[[city]]$trip_scen_sets %>% 
  mutate(scenario = case_when(
    scenario == "Scenario 1" ~ "CYC_SC", 
    scenario == "Scenario 2" ~ "CAR_SC",
    scenario == "Scenario 3" ~ "BUS_SC",
    scenario == "Scenario 4" ~ "MOT_SC",
    scenario == "Baseline" ~ "Baseline")) %>% 
  group_by(scenario, trip_mode, trip_distance_cat) %>% 
  summarise(n = dplyr::n(), dist = sum(trip_distance, na.rm = T)) %>% 
  mutate(city = city)

td <- dat[[city]]

for (i in 1:nrow(td)) {
    val <- td %>% filter(scenario == "Baseline", trip_mode == td$trip_mode[i] & 
                           trip_distance_cat == td$trip_distance_cat[i] &
                           city == td$city[i])
    
    if (nrow(val) > 0) {
      td$diff[i] <- val$n - td$n[i]
      td$trip_prop[i] <- round(td$n[i] / val$n, 2)
      td$dist_prop[i] <- round(td$dist[i] / val$dist, 2)
      
    }
}

dat[[city]] <- td

}

write_csv(bind_rows(dat), "results/multi_city/scen_prop.csv")

```

## Case study specific propensities
```{r message=F, error=F, warning=FALSE}
get_scen_settings <- ithimr::get_scenario_settings()

```

## Trip proportion
Case study specific trip proportions by mode, for baseline and four scenarios


```{r load_tidyverse, echo = F, message = F}
suppressWarnings({
  require(tidyverse)  
})
```


```{r trip_mode_dist = "asis", echo = F}

trip_prop <- list()

for (city in cities) { # Loop for each city
  df <- io[[city]]$trip_scen_sets
  u_trips <- df %>% dplyr::filter(scenario == "Baseline") %>% 
    summarise(uid = n_distinct(trip_id)) %>% as.numeric()
  td <- df %>% distinct(trip_id, scenario, .keep_all = T) %>% 
    group_by(trip_mode, scenario) %>% 
    summarise(p = round(dplyr::n() / u_trips * 100, 1)) %>% 
    spread(key = trip_mode, value = p) %>% 
    mutate(row_sums = rowSums(.[sapply(., is.numeric)], na.rm = TRUE))
  td <- as.data.frame(t(td))
  names(td) <- lapply(append('BASELINE', rownames(scen_prop)), as.character)
  td <- td[-1, ]
  x <- match(row.names(td), trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]
  
  td1 <- td %>% rownames_to_column()
  
  names(td1)[1] <- 'stage_mode'
  
  if (length(trip_prop) == 0){
    trip_prop <- td1 %>% dplyr::select(stage_mode)
  }
  
  td1 <- td1 %>% dplyr::select(stage_mode, BASELINE)
  
  names(td1)[2] <- city
  
  trip_prop <- inner_join(trip_prop, td1, by = 'stage_mode')
  
  print(kable(td, caption = paste("Trip proportion (%) by mode for ", city)))
  cat("\n")
} # End loop city

```


### Baseline trip proportion (%)
```{r}

trip_prop <- trip_prop %>% dplyr::filter(stage_mode != "row_sums") %>%
  mutate_at(2:ncol(trip_prop), ~ as.numeric(as.character(.x))) %>%
  janitor::adorn_totals('row')

kable(trip_prop, caption = 'Trip prop (%) for all case studies - only selected modes')

```

```{r unload_tidyverse, echo = F, message = F}
suppressWarnings({
  detach("package:tidyverse", character.only = T)
})

```

## Distance tables
Case study specific distance tables for baseline and four scenarios


```{r trip_dist = "asis"}

trip_dist <- list()

for (city in cities) {
  
  count_people <- nrow(io[[city]]$synth_pop)
  td <- io[[city]]$dist %>% dplyr::filter(stage_mode != 'bus_driver') %>%
    mutate_if(is.numeric, round, digits = round_to) %>% 
    mutate_if(is.numeric, list(~round((.) / count_people, round_to)))
  #colnames(td)[3:7] <- rownames(scen_prop)
  colnames(td)[2:ncol(td)] <- c("BASELINE", rownames(scen_prop))
  
  x <- match(td$stage_mode, trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]
  row.names(td) <- NULL
  
  print(kable(td, caption = paste("Distance table (km) per day for ", city, "( ", count_people, " ) per person")))
  cat("\n")
  
  td1 <- td
  
  if (length(trip_dist) == 0){
    trip_dist <- td1 %>% dplyr::select(stage_mode)
  }
  
  td1 <- td1 %>% dplyr::select(stage_mode, BASELINE)
  
  names(td1)[2] <- city
  
  trip_dist <- inner_join(trip_dist, td1, by = 'stage_mode')
  
  
  count_people <- length(unique(io[[city]]$trip_scen_sets$participant_id))
  td <- io[[city]]$dist %>% dplyr::filter(stage_mode != 'bus_driver') %>%
    mutate_if(is.numeric, round, digits = round_to) %>% 
    mutate_if(is.numeric, list(~round((.) / count_people, round_to)))
  #colnames(td)[3:7] <- rownames(scen_prop)
  colnames(td)[2:ncol(td)] <- c("BASELINE", rownames(scen_prop))
  x <- match(td$stage_mode, trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]
  row.names(td) <- NULL
  
  print(kable(td, caption = paste("Distance table (km) for ", city, "( ", count_people, " ) per person (people with trips)")))
  
}

```


### Baseline average distance (km) per day for all case studies
```{r}

trip_dist <- trip_dist %>% janitor::adorn_totals('row')

kable(trip_dist, caption = "Avg. distance per person (km) per day across all case studies")

```

## Distance tables scaled by using total population (per year in km)
Case study specific distance tables for baseline and four scenarios


```{r trip_tot_dist = "asis", message=F}

bl_td <- list()

for (city in cities) {
  
  count_people <- round(sum(io[[city]]$demographic$population))
  td <- io[[city]]$true_dist %>% dplyr::filter(stage_mode != 'bus_driver') %>%
    mutate_if(is.numeric, list(~round((.) * 365, 3)))
  #colnames(td)[3:7] <- rownames(scen_prop)
  colnames(td)[2:ncol(td)] <- c("BASELINE", rownames(scen_prop))
  
  # 
  
  x <- match(td$stage_mode, trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]
  row.names(td) <- NULL
  
  if (length(bl_td) == 0){
    bl_td <- td %>% dplyr::select(stage_mode)
  }
  
  td <- td %>% ungroup() %>% janitor::adorn_totals(c('row', 'col'))
  
  td1 <- td %>% dplyr::select(stage_mode, BASELINE)
  
  names(td1)[2] <- city
  
  bl_td <- inner_join(bl_td, td1, by = 'stage_mode')
  
  td1 <- td %>% gt() %>% fmt_number(columns = 2:ncol(td), decimals = T, suffixing = T)
  
  print(td1)
  
  # print(kable(td, caption = paste("Distance table (km) for ", city, "( ", sitools::f2si(count_people), " ) per person")))
  cat("\n")
  
}

```



### Baseline total distance for all case studies (per year in km)


```{r trip_dist_all_cities = "asis", message=F}

# tab <- bl_td %>% gt() %>% fmt_number(columns = 2:ncol(bl_td), decimals = T, suffixing = T)

backup <- bl_td

td <- as.data.frame(bl_td) %>% janitor::adorn_totals('row')

for (i in 2:ncol(td)){
  td[, i] <- comprss(td[, i])
  
}

print(kable(td, caption = paste("Distance table (km)")))


```


## Distance by distance category
### Tables

```{r trip_dist_mode_figs = "asis"}

for (city in cities){
  
  df <- io[[city]]$trip_scen_sets %>% dplyr::filter(scenario == 'Baseline') %>% distinct(trip_id, .keep_all = T) %>% group_by(trip_distance_cat) %>% summarise(sum_dist = sum(trip_distance), n_vals = dplyr::n(), prop = round(n_vals / nrow(.) * 100, 1))
  print(kable(df, caption = paste("Distance by mode by for  ", city)))
}

```


## True Distance by total population (per day in km)
### Tables

```{r trip_dist_mode_figs = "asis"}

for (city in cities){
  
  df <- io[[city]]$true_dist
  
  names(df)[-1] <- lapply(append('BASELINE', rownames(scen_prop)), as.character)
  
  print(kable(df, caption = paste("True distance by mode per day for  ", city)))
}

```


<!-- ### Figures -->

<!-- ```{r trip_dist_mode_figs = "asis"} -->

<!-- for (city in cities){ -->

<!--   df <- io[[city]]$trip_scen_sets %>% filter(scenario == 'Baseline' & trip_mode %in% c('walking', 'bicycle', 'car', 'motorcycle', 'bus')) %>% distinct(trip_id, .keep_all = T) %>% group_by(trip_mode, trip_distance_cat) %>% summarise(sum_dist = sum(trip_distance), n_vals = n()) %>%  -->
<!--     group_by(trip_mode) %>% mutate(n_vals_1 = sum(n_vals)) %>%  -->
<!--     mutate(prop = round(n_vals/n_vals_1 * 100, 1)) -->

<!--   print(ggplot(data=df, aes(x=trip_distance_cat, y=prop)) + -->
<!--           geom_bar(stat="identity", fill="steelblue")+ -->
<!--           facet_wrap(vars(trip_mode)) + -->
<!--           geom_text(aes(label=prop), vjust = -0.3, size = 3.5)+ -->
<!--           theme_minimal() + -->
<!--           theme(panel.spacing = unit(2, "lines")) + -->
<!--           labs(title = paste(city, ' by dist by mode'))) -->
<!-- } -->




<!-- ``` -->


## Duration tables

Case study specific duration tables for baseline and four scenarios (per day in minutes)


```{r trip_dur = "asis"}

trip_dur <- list()

l <- list()


for(city in cities){
  count_people <- nrow(io[[city]]$synth_pop)
  td <- io[[city]]$dur %>% dplyr::filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, list(~round((.) / count_people, round_to)))
  #colnames(td)[3:7] <- rownames(scen_prop)
  colnames(td)[2:ncol(td)] <- c("BASELINE", rownames(scen_prop))
  x <- match(td$stage_mode, trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]
  row.names(td) <- NULL
  
  l[[city]] <- td
  
  td1 <- td
  
  if (length(trip_dur) == 0){
    trip_dur <- td1 %>% dplyr::select(stage_mode)
  }
  
  td1 <- td1 %>% dplyr::select(stage_mode, BASELINE)
  
  names(td1)[2] <- city

  trip_dur <- inner_join(trip_dur, td1, by = 'stage_mode')
  
  print(kable(td, caption = paste("Duration table (mins) per day for ", city, "( ", count_people, " ) per person (everyone)")))
  
  
  count_people <- length(unique(io[[city]]$trip_scen_sets$participant_id))
  td <- io[[city]]$dur %>% dplyr::filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, list(~round((.) / count_people, round_to)))
  #colnames(td)[3:7] <- rownames(scen_prop)
  colnames(td)[2:ncol(td)] <- c("BASELINE", rownames(scen_prop))
  x <- match(td$stage_mode, trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]
  row.names(td) <- NULL
  
  print(kable(td, caption = paste("Duration table (mins) per day for ", city, "( ", count_people, " ) per person (people with trips)")))
  cat("\n")
}

```

### Baseline average duration (mins) per day for all case studies
```{r}

trip_dur <- trip_dur %>% janitor::adorn_totals('row')

kable(trip_dur, caption = "Avg. duration per person (mins) per day across all case studies")

```

## Health outcomes

### Change in YLL {#change_YLL}
```{r scen_prop = "asis"}
injury_col <- which(colnames(io[[1]]$outcomes$hb$deaths) == 'scen1_deaths_inj')
ap_death_cols <- which(sapply(colnames(io[[1]]$outcomes$pathway_hb$deaths |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))),function(x)grepl('ap',as.character(x))))
ap_yll_cols <- which(sapply(colnames(io[[1]]$outcomes$pathway_hb$ylls  |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))),function(x)grepl('ap',as.character(x))))
pa_death_cols <- which(sapply(colnames(io[[1]]$outcomes$pathway_hb$deaths |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))),function(x)grepl('pa',as.character(x))))
pa_yll_cols <- which(sapply(colnames(io[[1]]$outcomes$pathway_hb$ylls |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))),function(x)grepl('pa',as.character(x))))
sum_and_round_and_print <- function(data, text = '') {
  data <- lapply(data, function(x) round(x, round_to))
  data <- lapply(data, function(x) rbind(x, Total = colSums(x)))
  for (city in cities) {
    print(kable(data[[city]], caption = paste(text, city)))
    cat("\n")
  }
}
round_and_print <- function(data,text=''){
  data <- lapply(data, function(x)round(x,round_to))
  for(city in cities) {
    print(kable(data[[city]], caption = paste(text, city)))
    cat("\n")
  }
}
scen_names <- rownames(scen_prop)
#yll_totals <- lapply(io,function(x){
yll_totals <- lapply(io[-2],function(x){
  temp <- sapply(1:NSCEN,function(y){
    xx <- x$outcomes$hb$ylls |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))
    xxx <- rowSums(xx[,seq(2 + y, ncol(xx), by = NSCEN)])
    sapply(sort(unique(xx$age_cat)),function(z)
      sum(xxx[xx$age_cat == z]))
  })
  colnames(temp) <- scen_names
  temp
})
sum_and_round_and_print(yll_totals,"Change in YLL total in ")
```

YLLs per 100,000 people by age group by scenario

### Change in YLLs per 100,000 {#change_YLL_age_100k}
```{r scen_prop = "asis"}
pop_by_age <- lapply(io[-2], function(x)
  sapply(unique(x$demographic$age), 
         function(y)
           sum(subset(x$demographic, age == y)$population)
         )
  )
yll_rates <- lapply(cities, function(x)
  rbind(yll_totals[[x]] / t(repmat(pop_by_age[[x]],NSCEN,1))*100000,
        Total = colSums(yll_totals[[x]])/rep(sum(pop_by_age[[x]]), 
                                             length = NSCEN)*100000
        )
  )
names(yll_rates) <- cities
round_and_print(yll_rates,"Change in YLLs per 100,000 in ")
```

YLLs per 100,000 people by gender by age group scenario

### Change in YLLs per 100,000 {#change_YLL_gender_age_100k}
```{r scen_prop = "asis"}
#yll_totals <- lapply(io,function(x){
yll_totals <- lapply(io[-2], function(x) {
  temp <- sapply(1:NSCEN,function(y){
    xx <- x$outcomes$hb$ylls |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))
    rowSums(xx[,seq(2 + y, ncol(xx), by = NSCEN)])
  })
  rownames(temp) <- apply(x$outcomes$hb$deaths[,c('sex','age_cat')], 1,
                          function(z)paste0(z[2], '_', z[1]))
  colnames(temp) <- scen_names
  temp
})
yll_rates <- lapply(cities, function(x)
  rbind(yll_totals[[x]][match(apply(io[[x]]$demographic[,c('sex','age')], 1,
                                    function(z) paste0(z[2],'_',z[1])), 
                              rownames(yll_totals[[x]])),] /
          t(repmat(io[[x]]$demographic$population,NSCEN,1)) * 100000,
        Total = colSums(yll_totals[[x]])/rep(sum(pop_by_age[[x]]),
                                             length = NSCEN) * 100000))
names(yll_rates) <- cities
round_and_print(yll_rates,"Change in YLLs per 100,000 in ")
```

### Change in YLLs due to injury {#change_yll_injury}
```{r}
injury_totals <- lapply(io[-2], function(x) {
  xx <- x$outcomes$hb$ylls |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))
  injury_col <- grep("inj", names(xx))[1] # Dan: This line is mine (not sure is ok)
  xxx <- sapply(1:NSCEN, function(y)
    sapply(sort(unique(xx$age_cat)), function(z)
      sum(xx[xx$age_cat == z, injury_col - 1 + y])))
  colnames(xxx) <- scen_names
  xxx
})
sum_and_round_and_print(injury_totals, "Change in YLLs due to injury in ")
```

### Change in YLLs due to PA {#change_yll_PA}
```{r}
pa_totals <- lapply(io[-2],function(x){
  xx <- x$outcomes$pathway_hb$ylls  |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))
  xxx <- sapply(1:NSCEN, function(y){
    xxx <- rowSums(xx[, pa_yll_cols[seq(y, length(pa_yll_cols), by = NSCEN)]])
    sapply(sort(unique(xx$age_cat)), function(z) sum(xxx[xx$age_cat == z]))
  })
  colnames(xxx) <- scen_names
  xxx
})
sum_and_round_and_print(pa_totals,"Change in YLLs due to PA in ")
```

### Change in YLLs due to AP {#change_yll_AP}
```{r}
ap_totals <- lapply(io[-2],function(x){
  xx <- x$outcomes$pathway_hb$ylls  |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))
  xxx <- sapply(1:NSCEN,function(y) {
    xxx <- rowSums(xx[, ap_yll_cols[seq(y, length(ap_yll_cols), by = NSCEN)]])
    sapply(sort(unique(xx$age_cat)), function(z) sum(xxx[xx$age_cat == z]))
  })
  colnames(xxx) <- scen_names
  xxx
})
sum_and_round_and_print(ap_totals,"Change in YLLs due to AP in ")
```

YLLs per 100,000 people by age group by scenario

### Change in YLLs due to injury per 100,000 {#change_yll_injury_100k}
```{r scen_prop = "asis"}
injury_rates <- lapply(cities, function(x)
  rbind(
    injury_totals[[x]]/t(repmat(pop_by_age[[x]],NSCEN,1)) * 100000,
    Total = colSums(injury_totals[[x]])/rep(sum(pop_by_age[[x]]),
                                            length = NSCEN) * 100000)
  )
names(injury_rates) <- cities
round_and_print(injury_rates,"Change in YLLs due to injury per 100,000 in ")
```

### Change in YLLs due to PA per 100,000 {#change_yll_PA_100k}
```{r}
pa_rates <- lapply(cities, function(x)
  rbind(
    pa_totals[[x]] / t(repmat(pop_by_age[[x]], NSCEN, 1)) * 100000,
    Total = colSums(pa_totals[[x]])/rep(sum(pop_by_age[[x]]),
                                        length = NSCEN) * 100000))
names(pa_rates) <- cities
round_and_print(pa_rates,"Change in YLLs due to PA per 100,000 in ")
```

### Change in YLLs due to injury AP 100,000 {#change_yll_AP_100k}
```{r}
ap_rates <- lapply(cities, function(x)
  rbind(
    ap_totals[[x]] / t(repmat(pop_by_age[[x]], NSCEN ,1)) * 100000,
    Total = colSums(ap_totals[[x]]) / rep(sum(pop_by_age[[x]]),
                                          length = NSCEN) * 100000))
names(ap_rates) <- cities
round_and_print(ap_rates,"Change in YLLs due to AP per 100,000 in ")
```

## BY DISEASE
Change in deaths total (for the city based on real population size) by scenario

### Change in deaths due to disease {#change_death_disease}
```{r}
disease_totals <- lapply(io[-2],function(x){
  xx <- x$outcomes$hb$deaths |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))
  xxx <- sapply(1:NSCEN,function(y){
    colSums(xx[, seq(y + 2, ncol(xx), by = NSCEN)])
  })
  colnames(xxx) <- scen_names
  rownames(xxx) <- gsub("scen1_deaths_", "", rownames(xxx))
  #rownames(xxx) <- sapply(rownames(xxx), function(y) gsub('scen1_', '', y))
  # rownames(xxx) <- c("PA_AllCauses", "PA_AP_IschemicHeartDisease",
  #                    "PA_Neoplasms",
  #                    "PA_AP_LungCancer", "AP_COPD", "PA_AP_Stroke",
  #                    "PA_AP_T2Diabetes", "AP_LowerRespiratoryInfections",
  #                    "PA_BreastCancer", "PA_ColonCancer", "PA_UterineCancer",
  #                    "Injuries")
  xxx
})
sum_and_round_and_print(disease_totals,"Change in deaths due to disease in ")
```

Change in deaths per 100,000 people by scenario

### Change in deaths due to disease per 100,000 {#change_death_disease_100k}
```{r scen_prop = "asis"}
disease_rates <- lapply(cities, function(x)
  rbind(
    disease_totals[[x]] / sum(pop_by_age[[x]]) * 100000,
    Total = colSums(disease_totals[[x]]) / rep(sum(pop_by_age[[x]]), 
                                               length = NSCEN)*100000))
names(disease_rates) <- cities
round_and_print(disease_rates,"Change in deaths due to disease per 100,000 in ")
```

Change in YLL total (for the city based on real population size) by scenario

### Change in YLL due to disease {#change_yll_disease}
```{r}
disease_totals <- lapply(io[-2],function(x){
  xx <- x$outcomes$hb$ylls |> dplyr::select(-c(ends_with("lb") | ends_with("ub")))
  xxx <- sapply(1:NSCEN,function(y) {
    colSums(xx[,seq(y + 2, ncol(xx), by = NSCEN)])
  })
  colnames(xxx) <- scen_names
  rownames(xxx) <- gsub("scen1_ylls_", "", rownames(xxx))
  #rownames(xxx) <- sapply(rownames(xxx), function(y) gsub('scen1_','',y))
  # rownames(xxx) <- c("PA_AllCauses", "PA_AP_IschemicHeartDisease",
  #                    "PA_Neoplasms",
  #                    "PA_AP_LungCancer", "AP_COPD", "PA_AP_Stroke",
  #                    "PA_AP_T2Diabetes", "AP_LowerRespiratoryInfections",
  #                    "PA_BreastCancer", "PA_ColonCancer", "PA_UterineCancer",
  #                    "Injuries")
  xxx
})
sum_and_round_and_print(disease_totals,"Change in YLL due to disease in ")
```

### Change in YLL due to disease per 100,000 {#change_yll_disease_100k}
```{r scen_prop = "asis"}
disease_rates <- lapply(cities, function(x)
  rbind(
    disease_totals[[x]] / sum(pop_by_age[[x]]) * 100000,
    Total = colSums(disease_totals[[x]]) / rep(sum(pop_by_age[[x]]),
                                               length = NSCEN) * 100000))
names(disease_rates) <- cities
round_and_print(disease_rates,"Change in YLL due to disease per 100,000 in ")
```

```{r, echo=FALSE, results='hide', message=FALSE}
# Export all health results
health <- list()
measure <- c("ylls", "deaths")
pathway <- c("hb", "pathway_hb")
for (k in measure) { # loop for ylls or deaths
  for (j in pathway) { # loop for hb or pathway_hb
    for (i in names(io[-2])) { # loop for cities
      # Temporal datset
      temp <- io[[i]]$outcomes[[j]][[k]]
      # Population by age, and age-sex
      pop_by_age <- io[[i]]$demographic %>% group_by(age) %>% 
        summarize(pop_age = sum(population))
      pop_by_age_sex <- io[[i]]$demographic %>% group_by(age, sex) %>% 
        summarize(pop_age_sex = sum(population))
      
      # Long format and adding new variables
      health[[k]][[j]][[i]] <- gather(temp, key = "cause", "measure", 
                                      -sex, -age_cat) %>% 
        mutate(city = i,
               scenario = case_when(
                 grepl("scen1", cause) ~ scen_names[1],
                 grepl("scen2", cause) ~ scen_names[2],
                 grepl("scen3", cause) ~ scen_names[3],
                 grepl("scen4", cause) ~ scen_names[4],
                 grepl("scen5", cause) ~ scen_names[5],
               ),
               level1 = case_when(
                 grepl("all_cause", cause) ~ "L1: All Cause",
                 grepl("inj", cause) ~ "L1: RTI"
               ),
               level2 = case_when(
                 grepl("total_cancer", cause) ~ "L2: Cancer",
                 grepl("CVD", cause) ~ "L2: CVD",
                 grepl("COPD", cause) ~ "L2: Respiratory",
                 grepl("LRI", cause) ~ "L2: Respiratory",
                 grepl("T2D", cause) ~ "L2: Other",
                 grepl("total_dementia", cause) ~ "L2: Other",
                 grepl("Parkinson", cause) ~ "L2: Other",
                 grepl("inj", cause) ~ "L2: RTI"
               ),
               level3 = case_when(
                 grepl("IHD", cause) ~ "L3: IHD",
                 grepl("lung_cancer", cause) ~ "L3: lung_cancer",
                 grepl("COPD", cause) ~ "L3: COPD",
                 grepl("stroke", cause) ~ "L3: stroke",
                 grepl("T2D", cause) ~ "L3: T2D",
                 grepl("LRI", cause) ~ "L3: LRI",
                 grepl("breast_cancer", cause) ~ "L3: breast_cancer",
                 grepl("colon_cancer", cause) ~ "L3: colon_cancer",
                 grepl("endo_cancer", cause) ~ "L3: endo_cancer",
                 grepl("liver_cancer", cause) ~ "L3: liver_cancer",
                 grepl("total_dementia", cause) ~ "L3: total_dementia",
                 grepl("myeloma", cause) ~ "L3: myeloma",
                 grepl("Parkinson", cause) ~ "L3: Parkinson",
                 grepl("head_neck_cancer", cause) ~ "L3: head_neck_cancer",
                 grepl("stomach_cancer", cause) ~ "L3: stomach_cancer",
                 grepl("inj", cause) ~ "L3: RTI"
               ),
               dose = case_when(
                 grepl("_pa_ap_", cause) ~ "PA and AP",
                 grepl("_pa_", cause) ~ "PA",
                 grepl("_ap_", cause) ~ "AP",
                 grepl("_inj", cause) ~ "RTI"
               )
        ) %>% # End mutate 
        left_join(pop_by_age, by = c("age_cat" = "age")) %>% 
        left_join(pop_by_age_sex, by = c("age_cat" = "age", "sex" = "sex")) %>% 
        mutate(measure_100k = measure / pop_age * 100000,
               measeure_100k_sex = measure / pop_age_sex * 100000)
      
    } # Loop for each city
  } # Loop for each pathway
} # Loop for each measure
# # Export deaths HB
# path_deaths_wb <- "results/multi_city/health_impacts/Deaths.xlsx"
# deaths_wb <- readWorkbook(path_deaths_wb)
# wb <-  loadWorkbook(path_deaths_wb)
# removeTable(wb = wb, sheet = "Deaths", table = "Tabla1")
# writeDataTable(wb, sheet = "Deaths", x = rbindlist(health$deaths$hb, use.names = T), tableName = "Tabla1", startCol = 1)
# removeTable(wb = wb, sheet = "Deaths_Pathway", table = "Tabla2")
# writeDataTable(wb, sheet = "Deaths_Pathway", x = rbindlist(health$deaths$pathway_hb, use.names = T), tableName = "Tabla2", startCol = 1)
# saveWorkbook(wb, path_deaths_wb, overwrite =TRUE)
# 
# # Export ylls HB
# path_ylls_wb <- "results/multi_city/health_impacts/YLLs.xlsx"
# ylls_wb <- readWorkbook(path_ylls_wb)
# wb <-  loadWorkbook(path_ylls_wb)
# removeTable(wb = wb, sheet = "YLLs", table = "Tabla1")
# writeDataTable(wb, sheet = "YLLs", x = rbindlist(health$ylls$hb, use.names = T), tableName = "Tabla1", startCol = 1)
# removeTable(wb = wb, sheet = "YLLs_Pathway", table = "Tabla2")
# writeDataTable(wb, sheet = "YLLs_Pathway", x = rbindlist(health$ylls$pathway_hb, use.names = T), tableName = "Tabla2", startCol = 1)
# saveWorkbook(wb, path_ylls_wb, overwrite =TRUE)
# 

# Remove CIs
ylls <-  rbindlist(health$ylls$hb, use.names = T) |> filter(!str_detect(cause, "_lb") & !str_detect(cause, "_ub"))
ylls_pathway <- rbindlist(health$ylls$pathway_hb, use.names = T) |> filter(!str_detect(cause, "_lb") & !str_detect(cause, "_ub"))
deaths <- rbindlist(health$deaths$hb, use.names = T)|> filter(!str_detect(cause, "_lb") & !str_detect(cause, "_ub"))
deaths_pathway <- rbindlist(health$deaths$pathway_hb, use.names = T) |> filter(!str_detect(cause, "_lb") & !str_detect(cause, "_ub"))


# Export ylls HB
output_file <- "results/multi_city/health_impacts/data.xlsx"
writexl::write_xlsx(list(ylls = ylls,
                         ylls_pathway = ylls_pathway,
                         deaths = deaths,
                         deaths_pathway = deaths_pathway), 
                    path = output_file)
 
# Export ylls HB
write.csv(ylls,
            "results/multi_city/health_impacts/ylls.csv",
            row.names = F)
# Export ylls PATHWAY_HB
write.csv(ylls_pathway,
            "results/multi_city/health_impacts/ylls_pathway.csv",
            row.names = F)
# Export deaths HB
write.csv(deaths,
            "results/multi_city/health_impacts/deaths.csv",
            row.names = F)
# Export deaths PATHWAY_HB
write.csv(deaths_pathway,
            "results/multi_city/health_impacts/deaths_pathway.csv",
            row.names = F)


```

## PA dist
```{r}
### pa distr
cities <- names(io)[!names(io) %in% 'scen_prop']
l <- list()
for (city in cities){
  
  # city <- "antofagasta"
  
  td <- io[[city]]$outcomes$mmets %>% dplyr::select(ends_with("mmet")) %>%
    rename("Baseline" = base_mmet, "CYC_SC" = scen1_mmet,
           "CAR_SC" = scen2_mmet,  "BUS_SC" = scen3_mmet) %>% 
    summarise(across(, ~ quantile(.x, c(0.05,0.10,0.25, 0.375, 0.50,0.75,0.90), na.rm = T)), 
              prob = c(0.05,0.10,0.25, 0.375, 0.50,0.75,0.90)) %>%
    pivot_longer(cols = -c(prob)) %>% mutate(city = city)
  
  td1 <- io[[city]]$outcomes$mmets %>% dplyr::select(ends_with("mmet")) %>%
    rename("Baseline" = base_mmet, "CYC_SC" = scen1_mmet,
           "CAR_SC" = scen2_mmet,  "BUS_SC" = scen3_mmet) %>% 
    summarise(across(, ~ mean(.x))) %>%  t() %>% as.data.frame() %>% 
    tibble::rownames_to_column("name") %>% 
    rename(value = V1) %>% 
    mutate(prob = "mean") %>% mutate(city = city)
  
  l[[city]] <- plyr::rbind.fill(td, td1)
  
  
}
write_csv(data.table::rbindlist(l), "results/multi_city/PA/pa_distr.csv")
```