---
title: "Summary Tables"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment=NA, prompt=FALSE, cache=FALSE, echo=F, results='asis')

```

```{r helper_functions, echo = F, message = F}

# Source: https://stackoverflow.com/questions/28159936/formatting-large-currency-or-dollar-values-to-millions-billions
comprss <- function(tx) { 
  div <- findInterval(as.numeric(gsub("\\,", "", tx)), 
                      c(0, 1e3, 1e6, 1e9, 1e12) )  # modify this if negative numbers are possible
  paste(round( as.numeric(gsub("\\,","",tx))/10^(3*(div-1)), 2), 
        c("","K","M","B","T")[div] )
}

```

```{r loadLibraries, echo = F, message = F}
suppressWarnings({

library(summarytools)
library(knitr)
library(summarytools)
library(tidyverse)
})

st_options(bootstrap.css     = FALSE,       # Already part of the theme so no need for it
           plain.ascii       = FALSE,       # One of the essential settings
           style             = "rmarkdown", # Idem.
           dfSummary.silent  = TRUE,        # Suppresses messages about temporary files
           footnote          = NA,          # Keeping the results minimalistic
           subtitle.emphasis = FALSE)       # For the vignette theme, this gives
                                            # much better results. Your mileage may vary

```

```{r load_objects = "asis", echo = F, message = F}
io <- readRDS("results/multi_city/io.rds")
# Assumes that multi_city_script.R has been run till 
# Get names of cities from the io object
cities <- names(io)[!names(io) %in% 'scen_prop']

#cities <- c('accra','sao_paulo','buenos_aires')

# cities <- c('sao_paulo')

# Read trip_order
trip_order <- read_csv("data/global/trips/mode_order.csv")

# round to
round_to <- 1

# Set plot_mmets to F
plot_mmets <- F

```

## Scenario definition
Table displays highest propensity for each distance category, for a given mode.

Table displays highest propensity (%) for each distance category, for a given mode.

In scenario generation, trips are sampled without replacement to increase the share of the requested mode up to the total shown.

Distance categories are: 

0-1 km = \{trip distance < 2\}

2-5 km = \{2 <= trip distance < 6\}

6+ km = \{6 <= trip distance\}

```{r scen_prop = "asis"}

scen_prop <- round(io$scen_prop, round_to)

rownames(scen_prop) <- paste(rownames(io$scen_prop), "scen", sep = "_")

kable(scen_prop, headings = "Scenario Proportions")

```

## Case study specific propensities


|accra|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 98.5|0.0|0.0 |
| cycle | 0.5|1.5|0.4 |
| car | 0.8|29.8|14.4 |
| motorcycle | 0.0|0.1|1.0 |
| bus | 0.0|60.0|74.0 |

|bangalore|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 75.0|23.1|1.0 |
| cycle | 2.3|9.8|1.2 |
| car | 1.0|4.3|6.4 |
| motorcycle | 5.1|33.9|63.2 |
| bus | 15.1|24.3|24.9 |

|belo_horizonte|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 91.7|36.7|0.6 |
| cycle | 0.4|3.7|1.0 |
| car | 7.5|47.2|49.9 |
| motorcycle | 0.2|6.7|7.2 |
| bus | 0.1|4.8|37.5 |

|bogota|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 90.0|26.8|2.3 |
| cycle | 4.5|14.8|4.1 |
| car | 1.5|15.0|21.0 |
| motorcycle | 0.4|5.5|6.9 |
| bus | 3.1|33.5|61.0 |

|buenos_aires|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 96.6|34.2|0.1 |
| cycle | 2.3|8.3|1.0 |
| car | 0.5|24.4|21.8 |
| motorcycle | 0.0|1.9|1.2 |
| bus | 0.6|27.8|48.2 |

|cape_town|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 88.5|23.3|2.0 |
| cycle | 0.0|0.4|0.3 |
| car | 9.4|46.1|47.3 |
| motorcycle | 0.0|0.3|0.6 |
| bus | 2.0|27.5|36.5 |

|delhi|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 84.4|10.1|0.9 |
| cycle | 2.0|7.6|3.7 |
| car | 2.4|17.3|21.4 |
| motorcycle | 5.6|30.1|26.5 |
| bus | 0.7|24.7|32.7 |

|mexico_city|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 96.0|37.7|0.3 |
| cycle | 0.8|6.4|0.7 |
| car | 2.3|21.8|16.7 |
| motorcycle | 0.0|2.7|1.1 |
| bus | 0.4|24.3|58.0 |

|santiago|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 88.5|23.7|0.2 |
| cycle | 3.5|8.8|1.9 |
| car | 7.2|49.5|32.3 |
| motorcycle | 0.1|1.6|1.0 |
| bus | 0.3|10.3|29.8 |

|sao_paulo|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 62.2|7.2|3.0 |
| cycle | 0.7|0.9|0.3 |
| car | 22.0|45.1|29.9 |
| motorcycle | 1.3|2.9|3.8 |
| bus | 13.3|39.2|32.7 |

|vizag|0-1 km|2-5 km|6+ km|
|---|---|---|---|
| pedestrian | 84.1|23.1|0.1 |
| cycle | 4.0|9.0|2.4 |
| car | 0.6|2.9|2.8 |
| motorcycle | 9.9|30.1|29.2 |
| bus | 1.3|34.8|65.4 |


## Trip proportion
Case study specific trip proportions by mode, for baseline and five scenarios


```{r load_tidyverse, echo = F, message = F}
suppressWarnings({
  require(tidyverse)  
})
```


```{r trip_mode_dist = "asis", echo = F}

trip_prop <- list()

for(city in cities){
  print(city)
  df <- io[[city]]$trip_scen_sets
  u_trips <- df %>% dplyr::filter(scenario == "Baseline") %>% summarise(uid <- n_distinct(trip_id)) %>% as.numeric()
  td <- df %>% distinct(trip_id, scenario, .keep_all = T) %>% group_by(trip_mode, scenario) %>% summarise(p = round(dplyr::n() / u_trips * 100, 1)) %>% spread(key = trip_mode, value = p) %>% mutate(row_sums = rowSums(.[sapply(., is.numeric)], na.rm = TRUE))
  td <- as.data.frame(t(td))
  names(td) <- lapply(append('baseline', rownames(scen_prop)), as.character)
  td <- td[-1, ]
  x <- match(row.names(td), trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]
  
  td1 <- td %>% rownames_to_column()
  
  names(td1)[1] <- 'stage_mode'
  
  if (length(trip_prop) == 0){
    trip_prop <- td1 %>% dplyr::select(stage_mode)
  }
  
  td1 <- td1 %>% dplyr::select(stage_mode, baseline)
  
  names(td1)[2] <- city
  
  trip_prop <- inner_join(trip_prop, td1, by = 'stage_mode')
  
  print(kable(td, caption = paste("Trip proportion (%) by mode for ", city)))
  cat("\n")
}

```


### Baseline trip proportion (%)
```{r}

trip_prop <- trip_prop %>% dplyr::filter(stage_mode != "row_sums") %>% mutate_at(2:ncol(trip_prop), ~ as.numeric(as.character(.x))) %>% janitor::adorn_totals('row')

kable(trip_prop, caption = 'Trip prop (%) for all case studies - only selected modes')

```

```{r unload_tidyverse, echo = F, message = F}
suppressWarnings({
  detach("package:tidyverse", character.only = T)
})

```

## Distance tables
Case study specific distance tables for baseline and five scenarios


```{r trip_dist = "asis"}

trip_dist <- list()

for(city in cities){
  
  count_people <- nrow(io[[city]]$synth_pop)
  td <- io[[city]]$dist %>% filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, list(~round((.) / count_people, round_to)))
  colnames(td)[3:7] <- rownames(scen_prop)
  
  x <- match(td$stage_mode, trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]
  row.names(td) <- NULL
  
  print(kable(td, caption = paste("Distance table (km) per day for ", city, "( ", count_people, " ) per person")))
  cat("\n")
  
  td1 <- td
  
  if (length(trip_dist) == 0){
    trip_dist <- td1 %>% dplyr::select(stage_mode)
  }
  
  td1 <- td1 %>% dplyr::select(stage_mode, Baseline)
  
  names(td1)[2] <- city
  
  trip_dist <- inner_join(trip_dist, td1, by = 'stage_mode')
  
  
  count_people <- length(unique(io[[city]]$trip_scen_sets$participant_id))
  td <- io[[city]]$dist %>% filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, list(~round((.) / count_people, round_to)))
  colnames(td)[3:7] <- rownames(scen_prop)
  x <- match(td$stage_mode, trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]
  row.names(td) <- NULL
  
  print(kable(td, caption = paste("Distance table (km) for ", city, "( ", count_people, " ) per person (people with trips)")))
  
}

```


### Baseline average distance (km) per day for all case studies
```{r}

trip_dist <- trip_dist %>% janitor::adorn_totals('row')

kable(trip_dist, caption = "Avg. distance per person (km) per day across all case studies")

```

## Distance tables scaled by using total population (per year in km)
Case study specific distance tables for baseline and five scenarios


```{r trip_tot_dist = "asis", message=F}

bl_td <- list()

require(gt)

for(city in cities){
  
  print(city)
  count_people <- round(sum(io[[city]]$demographic$population))
  td <- io[[city]]$true_dist %>% filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, list(~round((.) * 365, 3)))
  colnames(td)[3:7] <- rownames(scen_prop)
  
  # 
  
  x <- match(td$stage_mode, trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]
  row.names(td) <- NULL
  
  if (length(bl_td) == 0){
    bl_td <- td %>% dplyr::select(stage_mode)
  }
  
  td <- td %>% ungroup() %>% janitor::adorn_totals(c('row', 'col'))
  
  td1 <- td %>% dplyr::select(stage_mode, Baseline)
  
  names(td1)[2] <- city
  
  bl_td <- inner_join(bl_td, td1, by = 'stage_mode')
  
  td1 <- td %>% gt() %>% fmt_number(columns = 2:ncol(td), decimals = T, suffixing = T)
  
  print(td1)
  
  # print(kable(td, caption = paste("Distance table (km) for ", city, "( ", sitools::f2si(count_people), " ) per person")))
  cat("\n")
  
}

```



### Baseline total distance for all case studies (per year in km)


```{r trip_dist_all_cities = "asis", message=F}

# tab <- bl_td %>% gt() %>% fmt_number(columns = 2:ncol(bl_td), decimals = T, suffixing = T)

backup <- bl_td

td <- as.data.frame(bl_td) %>% janitor::adorn_totals('row')

for (i in 2:ncol(td)){
  td[, i] <- comprss(td[, i])
  
}

print(kable(td, caption = paste("Distance table (km)")))


```


## Distance by distance category
### Tables

```{r trip_dist_mode_figs = "asis"}

for (city in cities){
  
  df <- io[[city]]$trip_scen_sets %>% filter(scenario == 'Baseline') %>% distinct(trip_id, .keep_all = T) %>% group_by(trip_distance_cat) %>% summarise(sum_dist = sum(trip_distance), n_vals = dplyr::n(), prop = round(n_vals / nrow(.) * 100, 1))
  print(kable(df, caption = paste("Distance by mode by for  ", city)))
}

```


## True Distance by total population (per day in km)
### Tables

```{r trip_dist_mode_figs = "asis"}

for (city in cities){
  
  df <- io[[city]]$true_dist
  
  names(df)[-1] <- lapply(append('baseline', rownames(scen_prop)), as.character)
  
  print(kable(df, caption = paste("True distance by mode per day for  ", city)))
}

```


<!-- ### Figures -->

<!-- ```{r trip_dist_mode_figs = "asis"} -->

<!-- for (city in cities){ -->

<!--   df <- io[[city]]$trip_scen_sets %>% filter(scenario == 'Baseline' & trip_mode %in% c('walking', 'bicycle', 'car', 'motorcycle', 'bus')) %>% distinct(trip_id, .keep_all = T) %>% group_by(trip_mode, trip_distance_cat) %>% summarise(sum_dist = sum(trip_distance), n_vals = n()) %>%  -->
<!--     group_by(trip_mode) %>% mutate(n_vals_1 = sum(n_vals)) %>%  -->
<!--     mutate(prop = round(n_vals/n_vals_1 * 100, 1)) -->

<!--   print(ggplot(data=df, aes(x=trip_distance_cat, y=prop)) + -->
<!--           geom_bar(stat="identity", fill="steelblue")+ -->
<!--           facet_wrap(vars(trip_mode)) + -->
<!--           geom_text(aes(label=prop), vjust = -0.3, size = 3.5)+ -->
<!--           theme_minimal() + -->
<!--           theme(panel.spacing = unit(2, "lines")) + -->
<!--           labs(title = paste(city, ' by dist by mode'))) -->
<!-- } -->




<!-- ``` -->


## Duration tables
Case study specific duration tables for baseline and five scenarios (per day in km)


```{r trip_dur = "asis"}

trip_dur <- list()

l <- list()


for(city in cities){
  count_people <- nrow(io[[city]]$synth_pop)
  td <- io[[city]]$dur %>% filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, list(~round((.) / count_people, round_to)))
  colnames(td)[3:7] <- rownames(scen_prop)
  
  x <- match(td$stage_mode, trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]
  row.names(td) <- NULL
  
  l[[city]] <- td
  
  td1 <- td
  
  if (length(trip_dur) == 0){
    trip_dur <- td1 %>% dplyr::select(stage_mode)
  }
  
  td1 <- td1 %>% dplyr::select(stage_mode, Baseline)
  
  names(td1)[2] <- city

  trip_dur <- inner_join(trip_dur, td1, by = 'stage_mode')
  
  print(kable(td, caption = paste("Duration table (mins) per day for ", city, "( ", count_people, " ) per person (everyone)")))
  
  
  count_people <- length(unique(io[[city]]$trip_scen_sets$participant_id))
  td <- io[[city]]$dur %>% filter(stage_mode != 'bus_driver') %>% mutate_if(is.numeric, round, digits = round_to) %>% mutate_if(is.numeric, list(~round((.) / count_people, round_to)))
  colnames(td)[3:7] <- rownames(scen_prop)
  
  x <- match(td$stage_mode, trip_order$mode)
  x[!is.na(x)]
  td <- td[order(x),]
  row.names(td) <- NULL
  
  print(kable(td, caption = paste("Duration table (mins) per day for ", city, "( ", count_people, " ) per person (people with trips)")))
  cat("\n")
}

```

### Baseline average duration (mins) per day for all case studies
```{r}

trip_dur <- trip_dur %>% janitor::adorn_totals('row')

kable(trip_dur, caption = "Avg. duration per person (mins) per day across all case studies")

```
