---
title: "Practicals: Session 11"
subtitle: "Air pollution exposure assignment"
author: "Lambed Tatah and Ali Abbas"
engine: knitr
editor: visual
toc: true
lightbox: true
format: 
  html: 
    theme: cosmos
    embed-resources: true
    toc: true
    code-tools: true
    code-fold: false
    page-layout: full
    df-print: paged
    number-sections: true
---

# Setup and call the ithim object `io`

-   Yesterday, you ran the ITHIM model and saved the outputs in `io`. It has has now been called here

```{r read_io, message=FALSE, warning=FALSE}
# Read the RDS file
io <- readRDS("data/io.rds")
```

# Take a look at some AP relevant outputs in io

-   Explore the structure of the `io` object
    -   eg display the objects in:
        -   io (list),
        -   bogota (list),
        -   dis (table),
        -   dur (table),
        -   outcomes (list)

```{r explore_io, message=FALSE, warning=FALSE}
io$bogota$dis|>View()
```

# Individual AP (PM2.5) exposure depends on:

-   Background PM2.5 concentration
-   Exposure factor (scaling to micro-environment during travels)
-   Inhalation rate (activity dependent)

## Calculate changes in background AP (PM2.5) concentration

-   What do we need to estimate changes in background AP concentration?
    1.  Baseline background PM2.5 concentration
    2.  Transport share of PM2.5
    3.  Vehicle emission inventory
    4.  Relative change in vehicle travel distance
    5.  Combine the above variables

### 1. Baseline background PM2.5 concentration

-   We get values from https://www.who.int/data/gho/data/themes/air-pollution/who-air-quality-database
-   We assume an average value (ignoring spatial and temporal variations)
-   Remember that thee is advancement in these estimates
    -   better resolution maps ets

```{r background_pm, message=FALSE, warning=FALSE}
conc_base_pm <- 12.69
```

### 2. Transport share of PM2.5

-   Varies by city heydari 2020 (Shahram Heydari)

```{r trans_share, message=FALSE, warning=FALSE}
transport_share <- 0.42
```

### 3. Vehicle emission inventory

-   Focus on the modes relevant for our calculations

-   We use values from EDGAR (link)

    -   Gives emission from different vehicles on a would grip
    -   We average over a city

    ```{r emission_inventory, message=FALSE, warning=FALSE}

    io$bogota$vehicle_inventory |>
      filter(PM_emission_inventory != 0) |>
      filter(!(grepl("truck", stage_mode)))|>
      select(-CO2_emission_inventory, -speed)

    ```

### 4. Relative change in vehicle travel distance

-   Read the `trip` dataset from the `io` object

```{r read_trip_set, message=FALSE, warning=FALSE}
trips <- io$bogota
```

-   Calculate distance per person for motorcycle, car, bus

```{r ind_distance, message=FALSE, warning=FALSE}
trips |>
filter(stage_mode %in% c("car_driver", "bus_driver", "motorcycle"))|>
group_by(stage_mode, scenario) |> 
reframe(mean_dist = sum(______) / nrow(io$bogota$base_pop)) |> 
pivot_wider(names_from = stage_mode, values_from = mean_dist)|>
select(stage_mode, baseline)

```

-   Calculate the distance travelled by vehicles in the travel dataset at baseline

```{r data_vehicle_distance_baseline, message=FALSE, warning=FALSE}
trips |> 
  filter(stage_mode %in% c("car_driver", "motorcycle", "bus_driver"))|>
  group_by(stage_mode, scenario) |> 
  reframe(mean_dist = sum(______)) |> 
  pivot_wider(names_from = stage_mode, values_from = mean_dist)|>
  select(stage_mode, baseline)
    
```

-   Calculate the total distance travelled by vehicles in the city at baseline

```{r city_vehicle_distance_baseline, message=FALSE, warning=FALSE}
trips |> 
  filter(stage_mode %in% c("car_driver", "motorcycle", "bus_driver"))|>
  group_by(stage_mode, scenario) |> 
  reframe(mean_dist = sum(______) / nrow(io$bogota$base_pop)*sum(io$bogota$demographic$population)) |> 
  pivot_wider(names_from = stage_mode, values_from = mean_dist)|>
  select(stage_mode, baseline)
  
```

-   Calculate the total distance travelled by vehicles in the city for different scenarios

```{r city_vehicle_distance_scenario, message=FALSE, warning=FALSE}
trips |> 
  filter(stage_mode %in% c("car_driver", "motorcycle", "bus_driver"))|>
  group_by(stage_mode, scenario) |> 
  reframe(mean_dist = sum(______) / nrow(io$bogota$base_pop)*sum(io$bogota$demographic$population)) |> 
  pivot_wider(names_from = stage_mode, values_from = mean_dist)
  
```

### 5. Combine varaibles to calculate change in background PM2.5 concentration

-   Calculate the total distance travelled by vehicles in the city at baseline

```{r vehicle distance_baseline, message=FALSE, warning=FALSE}
non_transport_pm_conc <- PM_CONC_BASE * (1 - PM_TRANS_SHARE)
transport_pm_conc <- PM_TRANS_SHARE *PM_CONC_BASE * sum(trans_emissions[[SCEN[i]]], na.rm = T) / baseline_sum

conc <- non_transport_pm_conc + transport_pm_conc  

```

-   Visualise changes in pm.25 by concentration

```{r scenario_pm, message=FALSE, warning=FALSE}
background_pm = io$bogota$outcomes$scenario_pm
```

## Exposure factor (during travel)

-   Calibrates background pm2.5 to micro-environment???

```{r micro_environmental_exposure, message=FALSE, warning=FALSE}
exp_facs <- data.frame(
    stage_mode = c("car", "bus", "cycle", "pedestrian", "motorcycle"),
    e_rate = c(2.5, 1.9, 2.0, 1.6, 2.0)
  )
  
```

## Inividual inhalation rate

Calculate individual inhalation by activity type

```{r indiv_ventillation_rates, message=FALSE, warning=FALSE}
#Activities include; travel, sleep, leisure, other light_activities
#sleep_hours <- 8.3....leisure_hours <- 3.2.....light_hours <- 10.8


travel_pm_inhaled <- trip_set$stage_duration / (60 * DAY_TO_WEEK_TRAVEL_SCALAR) * trip_set$v_rate * trip_set$e_rate * trip_set$conc_pm

sleep_pm_inhaled = sleep_duration / 60 * v_rate_sleep * conc_pm

leisure_pm_inhaled = leisure_duration / 60 * v_rate_leisure * conc_pm

light_pm_inhaled = light_duration / 60 * v_rate_light * conc_pm

total_pm_inhaled = travel_pm_inhaled + sleep_pm_inhaled + leisure_pm_inhaled + light_pm_inhaled

conc_pm_inhaled = total_pm_inhaled / total_air_inhaled

```

Individual PM2.5 exposure - Distribution

```{r summary_stats, message=FALSE, warning=FALSE}
io$bogota

```
