---
title: "Practicals: session 13th"
subtitle: "Creating scenarios"
author: "Ali Abbas"
engine: knitr
editor: visual
toc: true
lightbox: true
format: 
  html: 
    theme: cosmos
    embed-resources: true
    toc: true
    code-tools: true
    code-fold: false
    page-layout: full
    df-print: paged
    number-sections: true
---

# Learning objectives:

In-depth look at the scenario generation with a better understanding of travel behaviour

```{r setup}
#| echo: false
#| warning: false
#| eval: true
#| message: false
library(tidyverse)
library(here)
library(gt)
library(plotly)
# Read io
io <- readRDS(here("results/multi_city/io.rds"))
# Read trips from the io object and remove ghost trips (with participant_id = 0)
trips <- io$bogota$trip_scen_sets |> filter(participant_id > 0)
# Set palette for gt table
global_palette <- "viridis" #c("#fee8c8", "#e34a33")


theme_set(theme_minimal(base_family = "Spline Sans"))
theme_update(
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(),
  axis.line.x = element_line(color = "grey80", linewidth = .4),
  axis.ticks.x = element_line(color = "grey80", linewidth = .4),
  axis.title.y = element_blank(),
  plot.margin = margin(10, 15, 10, 15)
)


scen_colours <- c("Baseline" = '#b15928',
                  "Cycling" = '#abdda4',
                  "Car" = '#d7191c',
                  "Bus" = '#2b83ba',
                  "Motorcycle" = '#fdae61')


mode_colours <- c("pedestrian" = '#99d8c9',
                  "cycle" = '#abdda4',
                  "car" = '#d7191c',
                  "bus" = '#2b83ba',
                  "motorcycle" = '#fdae61',
                  "other" = '#fee8c8')


```

# Baseline travel behaviour

## Trip distribution by mode

Before we get into scenario creation, let's have a close look at trips distribution in the travel behaviour

```{r}
#| warning: false
# Read in the trips dataset
trip_dist <- trips |>  
    # Keep unique trips id - ignoring stage level info
    distinct(trip_id, scenario, .keep_all = T) |> 
    # Remove ghost trips (vehicle trips)
    filter(participant_id > 0, 
           # Only look at the baseline travel diary
           scenario == "baseline") |> 
    # Count grouped data by trip mode
    count(trip_mode) |> 
    # Calculate frequency as proportion
    mutate(freq = n/sum(n)) |> 
    # Remove n
    dplyr::select(-n) |> 
    pivot_wider(names_from = trip_mode, values_from = freq)

trip_dist |> 
    # dplyr::select(-scenario) |> 
    gt() |> 
    fmt_percent(
      columns =  where(is.numeric),
      decimals = 1
    ) |> 
    data_color(columns = where(is.numeric), 
               domain = c(trip_dist |> as.numeric() |> min(na.rm = T), 
                          trip_dist |> as.numeric() |> max(na.rm = T)), 
             palette = global_palette) |> 
  tab_header(
          title = "Percentage Distribution by Trip Mode",
          subtitle = "Values represent percentages summing to 100"
        )


```

This shows that `bus` share is the highest with `r round(trip_dist$bus * 100, 1)`(%) and `other` with the lowest share `r round(trip_dist$other * 100, 1)`(%).

## Trip distribution by distance categories

### Distribution using Cumulative Distribution Function (CDF)

We have defined three distance categories, which are:

1.  Short trips within `2 km`

2.  Medium trips between `2` and `6 km`

3.  Long trips with `6+ km`.

They have been drawn from domain knowledge as well as from empirical distance distribution captured in many trip diary datasets. Do note that they are not fixed and can be user-defined in the parameters sheet. In this exercise, let's see how distances for `bus`, `car`, `cycle` and `pedestrian` trips are distributed.

```{r}
 plotly::ggplotly(ggplot(trips |> 
                           filter(scenario == "baseline", 
                                  stage_mode %in% c('bus', 'car', 
                                                    'cycle', 'pedestrian')), 
                         aes(x = stage_distance, color = stage_mode)) +
     stat_ecdf(geom = "step") +
     geom_vline(alpha = 0.3, xintercept = 2, linetype = "solid", color = "black") +
     geom_vline(alpha = 0.3, xintercept = 6, linetype = "solid", color = "black") +
     scale_colour_manual(values = mode_colours, name = "Travel Mode") +
     coord_cartesian(ylim = c(0, 1)) +
     labs(x = "Distance (km)", y = "Cumulative Distribution Function (CDF)",
          title = "Distribution of distance (km) by mode \n\n") +
     theme_minimal()) |> 
  plotly::add_annotations(text="2 km",
                  x = 1.2, 
                  y = 0, 
                  showarrow = TRUE,
                  textangle = -90, 
                  font=list(size = 10)) |> 
  plotly::add_annotations(text="6 km",
                  x = 5.2, 
                  y = 0, 
                  showarrow = TRUE,
                  textangle = -90, 
                  font = list(size = 10))
```

### Table with distance categories

```{r}
# Read in the trips dataset
trips_tbl <- trips |> 
  # Filter baseline trips
  filter(scenario == "baseline") |> 
  # Keep distinct trip - to ignore trips with multiple stages
  distinct(trip_id, .keep_all = T) |> 
  # Count trip_mode, scenario and trip_distance_cat
  count(trip_mode, scenario, trip_distance_cat) |>
  # Now group by trip_mode and scenario
  group_by(trip_mode, scenario) |>
  # Calculate proportion of each trip_distance_cat
  mutate(proportion = n / sum(n)) |>  
  # Remove count by trip_distance_cat
  dplyr::select(-n) |>
  ungroup() |>
  # Keep only complete rows
  complete(scenario, trip_mode, trip_distance_cat, fill = list(proportion = 0)) |> 
  # Convert from long to wide format
  pivot_wider(names_from = trip_distance_cat, values_from = proportion) 
  
trips_tbl |> 
  # Remove scenario as we only have baseline
  dplyr::select(-scenario) |> 
  # Create a gt table
  gt() |> 
  # Convert all numerics into percentages
  fmt_percent(
    columns =  where(is.numeric),
    decimals = 1
  ) |> 
  # Rename columns
  cols_label(
    trip_mode = "Travel Mode") |> 
  # Colour all numeric columns
  data_color(columns = where(is.numeric), 
             domain = c(0, 1), 
             palette = global_palette,
             apply_to = "fill") |> 
  # Add table headers
  tab_header(
    title = "Percentage Distribution by  Trip Distance Category",
    subtitle = "Values represent percentages summing to 100 per row"
  )
  
```

## How does it work under the hood?

### Example of `5%` increase in cycling mode

Assume that there are only two distance bands `A` and `B` and that `80%` of all `cycling` trips lie in distance band `A` and the remaining `20%` in distance band `B`. In terms of overall trips, assume that `60%` of all trips are in distance band `A` and `40%` in distance band `B`.

Let's assume we want to increase the `cycling` mode share by `5%` of all trips. Then, we need to convert:

-   `5% x 80% / 60% = 6.67%` of non-cycling trips in distance band `A` to cycling trips and

-   `5% x 20% / 40% = 2.5%` of non-cycling trips in distance band B to cycling trips.

-   Overall, this leads to an increase of `(5% x 80% / 60%) x 60%` + `(5% x 20% / 40%) * 40%` = `5%` of cycling trips, whilst preserving the cycling mode shares of `80%` in distance band `A` and `20%` in distance band `B` and preserving the total mode shares of `60%` in distance band `A` and `40%` in distance band `B`. The total number of trips is also preserved.

## Create a pedestrian scenario

In this exercise, let's create a scenario, independent of the `ithimr` package. Now that we have a good understanding of trip modes and their distances, let's modify some of the trips and calculate impact of it on physical activity. We will consider these:

-   the shortest distance category with distances less than `2` km and

-   Convert them to `pedestrian` trips.

-   Do note that since `pedestrian` trips already account for `92.2%`, as we saw in the previous exercise, so we shouldn't expect a substantial change in the PA volume.

```{r}
# get baseline trips for 15-69 year olds from io
trips_baseline <- trips |> 
  filter(scenario == "baseline", 
         participant_id > 0) 

trips_ped_scen <- trips_baseline

trips_ped_scen[trips_ped_scen$trip_distance_cat  == '0-2km' & trips_ped_scen$trip_mode != "pedestrian"]$trip_mode <- 'pedestrian'

trips_ped_scen[trips_ped_scen$trip_mode == "pedestrian"]$stage_mode <- 'pedestrian'

trips_ped_scen[trips_ped_scen$trip_mode == "pedestrian"]$stage_duration <- trips_ped_scen[trips_ped_scen$trip_mode == "pedestrian"]$stage_distance * 60 / 2.5

trips_ped_scen$scenario <- 'sc_ped'

# Create a trip set and name it `ntrips`
ntrips <- rbind(trips_baseline, trips_ped_scen)

active_travel_duration <- ntrips |> 
  mutate(
      # Rename walk_to_pt to pedestrian
      stage_mode = case_when(grepl("walk_to_pt", stage_mode) ~ 
                                  "pedestrian", TRUE ~ stage_mode), 
      # Chage stage_duration in minutes to hours            
      stage_duration = stage_duration / 60) |> 
  # Group by participant_id for each scenario
  group_by(participant_id, scenario) |> 
  # Calculate overall duration per person per week spent in active travel
  reframe(dur_cyc_hrs = sum(stage_duration[stage_mode == "cycle"]),
          dur_ped_hrs = sum(stage_duration[stage_mode == "pedestrian"]))
# Show top rows
head(active_travel_duration)
WALKING_MMET <- 2.5
CYCLING_MMET <- 5.8

travel_mmets <- 
  # Use active travel duration per person dataset
  active_travel_duration |> 
  # Group by participant_id and scenario
  group_by(participant_id, scenario) |> 
  reframe(total_travel_mmets = dur_cyc_hrs * (CYCLING_MMET) + 
            dur_ped_hrs * (WALKING_MMET)) 


mmets_pp <- travel_mmets |> 
  ## join it with participant id and bring the `work_ltpa_marg_met` column
  ## the stores background PA for each individual
  left_join(io$bogota$base_pop |> dplyr::select(participant_id, work_ltpa_marg_met))


mmets_pp_total <- mmets_pp |> 
  mutate(total_mmets = work_ltpa_marg_met + total_travel_mmets)

mmets_pp_total_wide <- mmets_pp_total |> 
  # Remove columns that we are not interested in
  dplyr::select(-c(total_travel_mmets, work_ltpa_marg_met)) |> 
  # Take values from scenario and the variable that holds total mmets
  pivot_wider(names_from = scenario, values_from = total_mmets)

head(mmets_pp_total_wide)
```

### 
